---
title: Simulation connectance richness
author: Alain Danet
output:
  bookdown::pdf_document2
always_allow_html: true
bibliography: references.bib
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.pos = "H",  # pdf mode
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE,
  fig.path="figures/"
)
```

```{r, results = FALSE}
library(targets)
library(tidyverse)
library(magrittr)
library(ggcorrplot)
library(cowplot)
library(here)
library(arrow)
library(piecewiseSEM)
library(semEff)
library(easystats)
library(glmmTMB)

library(rpart)
library(rpart.plot)
library(caret)
library(ipred)
library(kableExtra)

mytheme <- theme_cowplot(font_size = 8) +
background_grid() +
theme(legend.position = "bottom")
theme_set(mytheme)
source(here::here("R", "network_metrics.R"))
source(here::here("R", "string_replacements.R"))
```

# Introduction

Global change and its simultaneous increasing stressors constitute a major
threat to biodiversity and ecosystem functioning [@pachauri_climate_2015;
@simmons_refocusing_2021]. Among them, climate change is predicted to lead
dramatically more variable environments [@pachauri_climate_2015], adding to
other persistent stressors such as eutrophication [@maure_globally_2021, add
ref]. Understanding how environmental variability and eutrophication will
affects ecosystem stability is then a timely question.

Biodiversity, in terms of species richness, has been repeatedly shown to drive
higher temporal stability of ecological communities, across various taxa and
ecosystems. Species richness can dampen the effects of perturbations on the
temporal variability of community biomass because more diverse communities
contain species with more diversity of responses to perturbations, which
generates asynchrony in population fluctuations, thereby stabilizing community
biomass fluctuations [@loreau_species_2008; @thibaut_understanding_2013;
@zhao_biodiversity_2022]. In turn, the effects of human pressures on biotic
homogenization reported in various ecosystems [@buisson_toward_2013;
@muthukrishnan_invasive_2020; @saladin_rapid_2020] is another threat, which
might in turn affect dampens the effects of species richness on ecosystem
stability. However, the joint effects of external stressors such as
environmental variability and eutrophication and internal stressors such as the
loss response diversity has been rarely assessed in temporal stability areas.

The question of stressors can even become complex in multitrophic communities,
where species richness corresponds both to horizontal and vertical diversity.
Food-web structure has been shown to have tremendous effect on community
stability. The degree of generalism of predator was shown to modulate
stability-richness relationships [@thebault_trophic_2005]. The strength and
distribution of interaction strength was also shown to be strong driver of
community stability [@mccann_weak_1998]. Omnivory was also shown to drive higher
stability [@mccann_reevaluating_1997]. The effects of food-web structure on
ecosystem stability has been mostly assessed with small modules [but see
@eschenbrenner_diversity_nodate], and we know very little how food-web structure
affects the relationships between species richness and temporal stability in
complex food-webs.

Both stressors and food-web structure are expected to have different effects on
temporal stability. Stability of community biomass can itself be partitioned in
several components, i.e. population stability and population asynchrony
[@thibaut_understanding_2013; @zhao_biodiversity_2022]. Population stability can
be itself partioned in total biomass and population variability effect.
Population asynchrony can further be partioned in statistical averaging effect
and compensatory dynamics effects [@zhao_biodiversity_2022]. Partitioning
stability allows to better understand how food-web structure and external
factors affect stability. We expect that environmental variability will
primarily affect. For exemple, environmental stochasticity is expected to
primarily affect population variance. Productivity is expected to have two
effects on stability. First, productivity may increase species richness and
average trophic level by increasing the flux of biomass in the system
[@lindeman_trophic-dynamic_1942] but on the other side, the resulting higher growth rate
of primary producers may increase the population variability
[@binzer_interactive_2016] and thus decreases the temporal stability of
community biomass. Response diversity is expected to act primarily on
compensatory dynamics in the food-webs, as low response diversity will decrease
the effects. Higher connectance and interaction strength are expected to dampens
population variability but to lead to higher synchrony at the same time.

---
#Understanding the mechanisms that determine temporal
#stability of ecosystem functioning is a long standing
#question in Ecology [@may_will_1972; @angelis_stability_1975;
#@mccann_diversitystability_2000; @tilman_biodiversity_2006;
#@donohue_navigating_2016; @kefi_advancing_2019].
---

In this study, we investigated both the effects of stressors (productivity,
environnmental variability and response diversity) and of food-web structure
(connectance, average interaction strength, average trophic level) on species
richness-stability relationships. To do, we used a bioenergetic food-web model
[@yodzis_body_1992; @brose_allometric_2006; @delmas_simulations_2017] added to
environmental stochasticity.


```{r}
concept_cap <- "Food-web structure, response diversity and enviromental gradient
can modulate stability-richness relationships. (a & b) Food-web structure may
modulate stability-richness relationships additively (a) or interactively (b).
(c) Decrease in response diversity and increase in environmental variability
should dampen stability-richness relationships. While the loss of response
diversity should dampen the effect of species richness on asynchrony, the
increase in environmental variability should decrease primarily population
stability. (d) Increase in productivity should increase species richness
(trophic energy hypothesis) but also dampens the relationship between stability
and species richness (paradox of enrichment). (e) Summary of the framework, how
food-web structure and external perturbations modulate the effects of species
richness on community stability. More precisely, how they affect the different
components of stability: total biomass, population variability, statistical
averaging effects and compensatory dynamics."
```


```{r, fig.cap=concept_cap}
knitr::include_graphics(here("report", "figures", "conceptual_figures.pdf"))
```

```{r}
tribble(
  ~Type, ~`Food-web structure`, ~`Effect on stability-richness`,
  "Food-web structure", "Connectance", "Strengthen (Miele et al., 2016) / No effect (Thébault & Loreau, 2005)",
  "Food-web structure", "Omnivory", "Strengthen (Mccann et al., 1997)",
  "Food-web structure", "Interaction strength", "Destabilising (Mccann et al., 1998) / Stabilising in
  productive (Binzer et al., 2012; Binzer et al., 2016; Tabi et al., 2019)",
  "Response diversity", "", "Dampens",
  "Productivity", "", "Dampens (Binzer et al., 2012; Binzer et al., 2016; Tabi et al., 2019)",
  "Environmental variability", "", "Dampens",) %>%
kbl(caption = "Predictions of stability-richness relationship from the literature.") %>%
kable_styling()
```

\pagebreak

```{r, eval = FALSE}
tar_load(sim_prep)
# test for disconnected species
ti <- sim_prep %>%
  filter(max_tlvl > 1) %>%
  mutate(
    disconnected_prod = map_lgl(max_int_alive,
      # which species has no predator (colsum) is not a predator
      ~any(colSums(.x) == 0 & rowSums(.x) == 0)
    )
  )

ti %>%
  ggplot(aes(x = as.factor(disconnected_prod), y = stab_com)) +
  geom_boxplot()
```


```{r}
tar_load(sim_stab)
sim_stab %<>%
  mutate(
    sae_even = map_dbl(sae, ~.x["even"]),
    evenness_sae = map_dbl(sae, ~.x["eveness"]),
    sae_total = map_dbl(sae, ~.x["total"])
  )
tar_load(sim)
sim_ok <- sim %>%
  select(-stab_com, -async) %>%
  left_join(sim_stab) %>%
  mutate(inv_sum_pop_var = pop_stab / total_biomass)
```



```{r}
sim_sem <- sim_ok %>%
  filter(max_tlvl_alive > 1) %>%
  mutate(across(c(stab_com, async, pop_stab, total_biomass, inv_sum_pop_var, sae_even, evenness_sae, cpe_env, cpe_int), log, , .names = "log_{.col}")) %>%
  na.omit()
```

```{r}
summary(sim_sem$max_tlvl_alive)
```


```{r}
p_sim_rich_prod_fw_only <- sim_sem %>%
  mutate(stab_pop = 1/ avg_cv_sp) %>%
  filter(rho %in% c(0, 1)) %>%
  pivot_longer(
    c(stab_com, stab_pop, sync),
    names_to = "metric",
    values_to = "stab") %>%
  mutate(
    metric = var_replacement()[metric],
    rho = rho_replacement()[as.character(rho)]
  ) %>%
  ggplot(aes(x = log(richness), y = log(stab), color = factor(productivity))) +
  geom_point(alpha = .1, shape = 20) +
  geom_smooth(method = "lm") +
  facet_grid(rows = vars(metric), cols = vars(rho), scales = "free_y") +
  labs(
    color = "Productivity",
    x = "Species richness",
    y = "Stability component"
  ) +
  scale_x_continuous(
    sec.axis = sec_axis(~ . ,
      name = "Response diversity",
      breaks = NULL,
      labels = NULL)
  )
ggsave(
  filename = here("report", "figures", "p_sim_rich_prod_fw_only.png"),
  p_sim_rich_prod_fw_only,
  scale = 1.4,
  width = 88,
  height = 88 * 1,
  units = "mm"
)
colnames(sim_sem)
```

```{r}
p_sim_rich_prod_fw_only_cpe <- sim_sem %>%
  mutate(stab_pop = 1/ avg_cv_sp, ) %>%
  filter(rho %in% c(0, 1)) %>%
  pivot_longer(
    c(sae_total, cpe),
    names_to = "metric",
    values_to = "stab") %>%
  mutate(
    metric = var_replacement()[metric],
    rho = rho_replacement()[as.character(rho)]
  ) %>%
  ggplot(aes(x = log(richness), y = log(stab), color = factor(productivity))) +
  geom_point(alpha = .1, shape = 20) +
  geom_smooth(method = "lm") +
  facet_grid(rows = vars(metric), cols = vars(rho), scales = "free_y") +
  labs(
    color = "Productivity",
    x = "Species richness",
    y = "Stability component"
  ) +
  scale_x_continuous(
    sec.axis = sec_axis(~ . ,
      name = "Response diversity",
      breaks = NULL,
      labels = NULL)
  )
ggsave(
  filename = here("report", "figures", "p_sim_rich_prod_fw_only_cpe.png"),
  p_sim_rich_prod_fw_only_cpe,
  scale = 1.4,
  width = 88,
  height = 88 * 1,
  units = "mm"
)
```



```{r}
sem_list_basic <- list(
  w_avg_tlvl_alive = lm(w_avg_tlvl_alive ~ richness + ct_alive, sim_sem),
#  avg_omnivory = lm(avg_omnivory ~ richness + ct_alive + w_avg_tlvl_alive, sim_sem),
  sd_max_int_alive = lm(sd_max_int_alive ~ richness + ct_alive + w_avg_tlvl_alive + Z, sim_sem),
  avg_max_int_alive = lm(avg_max_int_alive ~ richness + ct_alive + w_avg_tlvl_alive + Z, sim_sem),
  log_inv_sum_pop_var = lm(log_inv_sum_pop_var ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive + env_stoch + rho, sim_sem),
  log_total_biomass = lm(log_total_biomass ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive + env_stoch + rho, sim_sem),
  log_sae_even = lm(log_sae_even ~ richness, sim_sem),
  log_evenness_sae = lm(log_evenness_sae ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive, sim_sem),
  log_cpe_env = lm(log_cpe_env ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive + rho + env_stoch, sim_sem),
  log_cpe_int = lm(log_cpe_int ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive, sim_sem),
  log_async = lm(log_async ~ log_sae_even + log_evenness_sae + log_cpe_env + log_cpe_int, sim_sem),
  #log_stab_pop = lm(log_pop_stab ~ log_total_biomass + log_inv_sum_pop_var, sim_sem),
  log_stab_com = lm(log_stab_com ~ log_total_biomass + log_inv_sum_pop_var + log_async, sim_sem)
)
sem_basic <- as.psem(sem_list_basic)
ti <- summary(sem_basic)$coefficients[, c(1, 2, 8, 9)]
colnames(ti)[4] <- "Signif"
ti
```
```{r, eval = FALSE}
lm(
  log_stab_com ~ log_total_biomass + log_inv_sum_pop_var + log_async,
  sim_ok %>%
    filter(ct_alive == 0) %>%
    mutate(across(c(stab_com, async, pop_stab, total_biomass, inv_sum_pop_var, sae_even, evenness_sae, cpe_env, cpe_int), log, , .names = "log_{.col}"))%>%
    mutate(across(where(is.double), ~scale(.x)[,1]))
)
```

```{r}
sim_ok %>%
  filter(max_tlvl_alive > 1)
```



```{r}
sim_stab %>%
  ggplot(aes(x = as.factor(rho), y = cpe_env)) +
  geom_boxplot() +
  geom_hline(yintercept = c(.5, 1))
sim_stab %>%
  ggplot(aes(x = as.factor(env_stoch), y = cpe_env)) +
  geom_boxplot() +
  geom_hline(yintercept = c(.5, 1))
sim_stab %>%
  ggplot(aes(x = as.factor(env_stoch), y = cpe)) +
  geom_boxplot() +
  geom_hline(yintercept = 1)

sim_stab %>%
  ggplot(aes(x = as.factor(env_stoch), y = stab_com)) +
  geom_boxplot() +
  geom_hline(yintercept = 1)
sim_stab %>%
  ggplot(aes(x = as.factor(rho), y = stab_com)) +
  geom_boxplot() +
  geom_hline(yintercept = 1)
sim_stab %>%
  ggplot(aes(x = as.factor(rho), y = evenness_sae)) +
  geom_boxplot() +
  geom_hline(yintercept = 1)
sim_ok %>%
  filter(max_tlvl_alive > 1) %>%
  ggplot(aes(x = as.factor(as.integer(richness)), y = evenness_sae)) +
  geom_boxplot() +
  geom_hline(yintercept = 1)
sim_ok %>%
  filter(max_tlvl_alive > 1) %>%
  ggplot(aes(x = as.factor(as.integer(max_tlvl_alive)), y = evenness_sae)) +
  geom_boxplot() +
  geom_hline(yintercept = 1)
sim_stab %>%
  ggplot(aes(x = as.factor(rho), y = sae_total)) +
  geom_boxplot() +
  geom_hline(yintercept = 1)

sim_stab %>%
  ggplot(aes(x = as.factor(env_stoch), y = sae_total)) +
  geom_boxplot() +
  geom_hline(yintercept = 1)
sim_stab %>%
  ggplot(aes(x = as.factor(env_stoch), y = evenness_sae)) +
  geom_boxplot() +
  geom_hline(yintercept = 1)

sim_stab %>%
  ggplot(aes(x = as.factor(env_stoch), y = pop_stab)) +
  geom_boxplot() +
  geom_hline(yintercept = 1)
sim_stab %>%
  ggplot(aes(x = as.factor(rho), y = pop_stab)) +
  geom_boxplot() +
  geom_hline(yintercept = 1)
```

```{r}
sim %>%
  filter(ct_alive != 0) %>%
  ggplot(aes(y = avg_omnivory, x = richness)) +
  geom_point()

sim %>%
  filter(ct_alive != 0) %>%
  ggplot(aes(y = avg_omnivory, x = ct_alive)) +
  geom_point()

sim %>%
  filter(ct_alive != 0) %>%
  ggplot(aes(x = avg_omnivory, y = 1/avg_cv_sp)) +
  geom_point()

sim %>%
  filter(ct_alive != 0) %>%
  ggplot(aes(x = avg_omnivory, y = sync)) +
  geom_point()

sim %>%
  filter(ct_alive != 0) %>%
  ggplot(aes(x = Z, y = max_tlvl_alive)) +
  geom_point()
```

```{r}
p_sim_sync_rich <- sim %>%
  filter(ct_alive != 0) %>%
  ggplot(aes(x = richness, y = sync, color = as.factor(env_stoch))) +
  geom_point() +
  geom_smooth() +
  facet_grid(cols = vars(productivity), rows = vars(rho))

p_sim_pop_rich <- sim %>%
  filter(ct_alive != 0) %>%
  ggplot(aes(x = richness, y = 1/avg_cv_sp, color = as.factor(env_stoch))) +
  geom_point() +
  geom_smooth() +
  facet_grid(cols = vars(productivity), rows = vars(rho))
```


```{r}
p_sim_stab_rich <- sim %>%
  filter(ct_alive != 0) %>%
  ggplot(aes(x = richness, y = stab_com, color = as.factor(env_stoch))) +
  geom_point() +
  geom_smooth() +
  facet_grid(cols = vars(productivity), rows = vars(rho))
ggsave(
  filename = here("report", "figures", "sim_stab_richnness_rho_stoch.pdf"),
  p_sim_stab_rich,
  width = 80,
  height = 80 * 4,
  units = "mm",
  scale = 2.4
)
```

```{r}
knitr::include_graphics(here::here("report", "figures", "sim_stab_richnness_rho_stoch.pdf"))
```






# Annexes

# Research questions

For me, there are two ways to see the question.

##  What are the mecanisms driving stability in food-webs ?

- How structure of food-webs (connectance, species richness, prey-predator
     size ratio) gives emergence to food-web structure (max trophic level,
     weighted avg trophic level, omnivory) ?
- How food-web structure influence biomass fluxes (avg interaction
     strength, sd of interaction strength, asymetry)?
- How food-web structure and biomass fluxes affect stability components?
     total biomass, species variability, statistical averaging, evenness,
     compensatory dynamics (interaction and environment)?

## What is the effects of species richness on stability facing multiple stressors in competitive and food-webs communities?

- How do species richness drive average population stability and asynchrony
  in competitive and food-webs communities ?
- How is it affected by enrichment and response diversity?

# Material & Methods


## Bioenergetic model

TO Complete

- Important bits:
  - Niche model (Connectance highly constrained by richness)
  - Type III functional response
  - No predator interference
  - Enrichment: K = 5 to 30
  - Standardized carrying capacity (Remove the effect of species richness on
    total biomass, i.e. remove the effect of niche complementarity on biomass
    produced by primary producers)

- Brose started with 5 basal species and K = 1, so his minimum total K is 5

## Variables

- S: 5 to 60
- C: .02 to .3
- K: 1 and 30
- $\rho$: 0 to 1
- $\sigma_e$: from 0.2 to 0.6
- Z: 5 to 1000


```{r}
cor_cap <- "Correlation among foodweb structure and stability for basic (a) and
enriched (b) environments."
```


```{r, fig.cap=cor_cap}
tar_read(p_cor)
```

# Effect of species richness

```{r, fig.cap = "Effect of stressors on community stability."}
tar_read(p_stab_s_stress)
```


- Enrichment decreases the effect of response diversity of stability
- Enrichment increases synchrony
- Richness decreases population stability, but increases it in absence of response
  diversity
- Food-web maintains some asynchrony despite the absence of response
  diversity but synchrony increase with richness in basic environment






```{r}
sim_sem_nodivresp <- simZ %>%
  filter(ct_alive != 0, env_stoch == 0.5, rho == 1) %>%
  mutate(across(c(async, stab_pop, stab_com, richness, ct_alive, sd_max_int_alive, avg_max_int_alive), log, , .names = "log_{.col}")) %>%
  mutate(
    log1_avg_max_int_alive = log(avg_max_int_alive + 1),
    log1_sd_max_int_alive = log(sd_max_int_alive + 1),
    productivity_f = factor(productivity)
    ) %>%
  as.data.frame()
```

```{r}
sem_list_nodivresp <- list(
  w_avg_tlvl_alive = lm(w_avg_tlvl_alive ~ richness + ct_alive, sim_sem_nodivresp),
  sd_max_int_alive = lm(sd_max_int_alive ~ richness + ct_alive + w_avg_tlvl_alive, sim_sem_nodivresp),
  avg_max_int_alive = lm(avg_max_int_alive ~ richness + ct_alive + w_avg_tlvl_alive, sim_sem_nodivresp),
  log_async = lm(log_async ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive, sim_sem_nodivresp),
  log_stab_pop = lm(log_stab_pop ~ richness + avg_max_int_alive + sd_max_int_alive + w_avg_tlvl_alive + ct_alive, sim_sem_nodivresp),
  log_stab_com = lm(log_stab_com ~ log_async + log_stab_pop, sim_sem_nodivresp)
)
sem_nodivresp <- as.psem(sem_list_nodivresp)
```

```{r}
coef_sem_nodivresp <- summary(sem_nodivresp)$coefficients[, c(1, 2, 8, 9)]
colnames(coef_sem_nodivresp)[4] <- "Signif"
coef_sem_nodivresp %>%
  mutate(
    Response = var_replacement()[Response],
    Predictor = var_replacement()[Predictor]
  ) %>%
  kable(caption = "Standardized estimates for the Structural Equation Models with no response diversity.") %>%
  collapse_rows(1, valign = "middle") %>%
  kable_styling()
```


# Effect of multiple stressors on stability in monotrophic and food-webs


```{r}
tar_load(p_mod_rho_scaled)
p_mod_rho_scaled_tot <- plot_grid(plotlist = p_mod_rho_scaled)
ggsave(here("report", "figures", "p_mod_rho_scaled_tot.pdf"),
  plot = p_mod_rho_scaled_tot,
  device = NULL,
  path = NULL,
  scale = 2.4,
  units = "mm",
  width = 140,
  height = 140 * .5,
  dpi = 300,
  limitsize = TRUE,
  bg = NULL
)
```


```{r, eval = FALSE}
tar_load(p_mod_rho)
plot_grid(plotlist = p_mod_rho)
```

```{r, eval = FALSE}
sim_rho
```


```{r}
tar_load(pred_rho)
p_pred_rho <- pred_rho %>%
  mutate(rho = rho_replacement()[as.character(rho)]) %>%
  ggplot(aes(
      y = log_stab_com,
      x = log_richness,
      color = factor(ct_alive),
      linewidth = factor(log1_avg_max_int_alive)
      )) +
  geom_line() +
  labs(
    color = "Connectance",
    linewidth = "Avg interaction strength",
    y = "Community stability",
    x = "Species richness (log)"
    ) +
  facet_grid(
    rows = vars(rho),
    cols = vars(productivity)
  )
ggsave(here("report", "figures", "p_pred_rho.pdf"),
  plot = p_pred_rho,
  device = NULL,
  path = NULL,
  scale = 2.4,
  units = "mm",
  width = 140,
  height = 140 * .5,
  dpi = 300,
  limitsize = TRUE,
  bg = NULL
)
```

```{r}
predS_cap <- "Predictions for the model of drivers of community stability in
basic and enriched environments (columns) and across varying response diversity
(rows)."
```

```{r predS, fig.cap = predS_cap}
knitr::include_graphics(here("report", "figures", "p_pred_rho.pdf"))
```


```{r}
coef_rho_cap <- "Coefficients for the model of drivers of community stability,
population stability and asynchrony. See predictions for a more simple overview."
```

```{r coef-rho, fig.cap = coef_rho_cap}
knitr::include_graphics(here("report", "figures", "p_mod_rho_scaled_tot.pdf"))
```

- From the predictions of the model:
  - Stong interaction among interaction strength, connectance and species
    richness, enrichment and response diversity = *Food-web structure effects on
    stability is context dependant*
  - High connectance and high interaction strength is generally destabilizing,
    driving negative relationships between stability and species richness in
    enrichment context (high $K$)
  - At the reverse, low connectance and high interaction strength is stabilizing
  - In basic environment, high interaction strength stabilise the community
    biomass in the absence of response diversity. At the opposite, low
    interaction strength generate a negative stability richness relationship.
  - In enrichment context, response diversity has little effect on stability!
  - In enrichment context, High interaction strength is generally stabilizing!


```{r, eval = FALSE}
mod_rho_tot <- glmmTMB(
  log_stab_com ~ log1_avg_max_int_alive*log_richness*ct_alive*rho*productivity +
    env_stoch + (1 | Z),
  sim_rho_scaled)
coef_mod_rho_tot <- model2tibble(mod_rho_tot)
coef_mod_rho_tot %>%
  ggplot(aes(y = parameter, x = coefficient, xmin = ci_low, xmax = ci_high)) +
  geom_pointrange() +
  labs(x = "Standardized Coefficients")
```

```{r, eval = FALSE}
sim_rho_pers <- simZ %>%
  mutate(across(c(S, ct, avg_max_int, gini_max_int), log, , .names = "log_{.col}")) %>%
  mutate(
    log1_avg_max_int = log(avg_max_int + 1),
    productivity_f = factor(productivity)
    ) %>%
  as.data.frame() %>%
  select(c(
      log_S, ct, max_tlvl, Z, rho,
      gini_max_int, avg_max_int, log1_avg_max_int, env_stoch,
      productivity, productivity_f,
      persistence)
  )
sim_rho_pers_scaled <- sim_rho_pers %>%
  mutate(across(where(is.double), ~scale(.x)[,1]))

pred_rho_pers <- "log1_avg_max_int * log_S * rho +
log1_avg_max_int * log_S * productivity +
log1_avg_max_int * log_S * ct +
log1_avg_max_int * ct * rho +
log1_avg_max_int * ct * rho +
log1_avg_max_int * ct * productivity +
log_S * rho * productivity +
log_S * ct * productivity +
log_S * ct * rho +
env_stoch"
rand <- "(1 | Z)"

mod_rho_pers <- glmmTMB(formula(paste0("persistence ~ ", pred_rho_pers, " + ", rand)),
  sim_rho_pers_scaled)

r2_nakagawa(mod_rho_pers)
plot(parameters(mod_rho_pers))
```

## Regression tree


```{r, eval = FALSE}
library(rpart)
library(rpart.plot)
set.seed(123)
m1 <- rpart(
  formula = log_stab_com ~ .,
  data    = sim_rho %>%
    select(log_stab_com, log_richness, ct_alive, rho, env_stoch,
      gini_max_int, max_tlvl_alive, log1_avg_max_int_alive, productivity),
  method  = "anova"
  )
rpart.plot(m1)
```

```{r, eval=FALSE}
bagged_m1 <- bagging(
  formula = log_stab_com ~ .,
  data    = sim_rho %>%
    select(log_stab_com, log_richness, ct_alive, rho, env_stoch,
      gini_max_int, max_tlvl_alive, log1_avg_max_int_alive, productivity),
  coob    = TRUE
)
```

```{r, eval = FALSE}
library(ipred)
ctrl <- trainControl(method = "cv",  number = 10)

# CV bagged model
bagged_cv <- train(
  Sale_Price ~ .,
  data = ames_train,
  method = "treebag",
  trControl = ctrl,
  importance = TRUE
  )
```

```{r, fig.cap = "Variable importance from bagged regression tree."}
ctrl <- trainControl(method = "cv",  number = 10)

# CV bagged model
bagged_cv <- train(
  stab_com ~ richness + ct_alive + max_tlvl_alive +
    w_avg_tlvl_alive + avg_max_int_alive + sd_max_int_alive + rho + productivity,
  data = simZ %>% filter(ct_alive != 0, avg_max_int_alive != 0),
  cp = .2,
  maxdepth = 6,
  method = "treebag",
  trControl = ctrl,
  importance = TRUE
  )
plot(varImp(bagged_cv), 8)
```

```{r, fig.cap="Regression tree "}
m1 <- rpart(
  formula = stab_com ~ richness + ct_alive + rho + productivity + w_avg_tlvl_alive + max_tlvl_alive +
    avg_max_int_alive + sd_max_int_alive,
  data    = simZ %>%
    filter(ct_alive != 0, avg_max_int_alive != 0),
  method  = "anova"
  )
rpart.plot(m1)
```

# Appendix

```{r}
sim_ok %>%
  ggplot(aes(x = as.factor(Z), y = max_tlvl_alive, color = as.factor(S))) +
  geom_boxplot() +
  facet_grid(cols = vars(productivity))
sim_ok %>%
  ggplot(aes(x = as.factor(Z), y = max_tlvl_alive, color = as.factor(S))) +
  geom_boxplot() +
  facet_grid(cols = vars(env_stoch), rows = vars(productivity))
sim_ok %>%
  ggplot(aes(x = as.factor(Z), y = avg_max_int_alive, color = as.factor(S))) +
  geom_boxplot() +
  facet_grid(cols = vars(productivity))

sim_ok %>%
  ggplot(aes(x = as.factor(Z), y = persistence, color = as.factor(S))) +
  geom_boxplot() +
  facet_grid(cols = vars(env_stoch), rows = vars(productivity))
sim_ok %>%
  ggplot(aes(x = as.factor(Z), y = pop_stab, color = as.factor(S))) +
  geom_boxplot() +
  facet_grid(cols = vars(env_stoch), rows = vars(productivity))
sim_ok %>%
  ggplot(aes(x = ct_alive, y = persistence, color = as.factor(S))) +
  geom_point()
```

- K = 1 is too low for meaningful food-webs, I should start with K = 5 as in
  Brose et al. (2006)
