---
title: "Target Markdown"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

Target Markdown is a powerful R Markdown interface for reproducible analysis
pipelines, and the chapter at https://books.ropensci.org/targets/markdown.html
walks through it in detail. This R Markdown report the example from the chapter.
Try it out in both interactive and non-interactive modes, either by running the
code chunks in different ways or setting the `tar_interactive` chunk option.

# Packages

The example requires several R packages, and `targets` must be version 0.5.0.9000 or above.

```{r, eval = FALSE}
install.packages(c("biglm", "dplyr", "ggplot2", "readr", "targets", "tidyr"))
```

# Setup

If you are using old versions of `targets` (<= 0.7.0) and/or `knitr` (<= 1.33), you will need to load the `targets` package in the R Markdown document in order for Target Markdown code chunks to work.

```{r}
library(targets)
```

Near the top of the document, you may also wish to remove the `_targets_r` directory previously written by non-interactive runs of the report. Otherwise, your pipeline may contain superfluous targets.

```{r}
library(targets)
tar_unscript()
```

# Globals

We first define some global options/functions common to all targets. The function below plots a histogram of ozone concentrations, and our histogram target will need it.

```{targets example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
tar_option_set(packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra"))
source(here::here("R", "network_metrics.R"))
source(here::here("R", "string_replacements.R"))
source(here::here("R", "stability_decomposition.R"))
source(here::here("R", "model_helpers.R"))
source(here::here("R", "sem_helpers.R"))
```


# Targets

Our first target borrows the `airquality` dataset built into base R.

```{targets raw-data}
list(
  tar_target(sim_list, {
    sim_files <- list.files(here("res", "simCSZenrich"))
    map(sim_files,
      function (x) {
        open_dataset(here::here("res", "simCSZenrich", x),
          format = "arrow") %>%
        collect()
      })
}
    ),
  tar_target(simZ_prep,
    map_dfr(sim_list,
      function (x) {
        x %>%
          # Remove simulation that have failed to run
          filter(!is.na(richness)) %>%
          # Transform back interaction strength into matrices
          mutate(across(where(is.list), as.list)) %>%
          mutate(across(c(int_strength, max_int),
              ~map2(.x, S,
                function(y, rich) {
                  matrix(y, nrow = rich)
                }
              )
          )
            ) %>%
          # Get matrix of alive species
          mutate(max_int_alive  = map2(max_int, bm_sp,
              function(mat, bm) {
                mask <- bm > 10^-6
                mat[mask, mask, drop = FALSE]
              }
            )
          )
      }
    )
    ),
  tar_target(simZ,
    simZ_prep %>%
      mutate(
        persistence = richness / S,
        async = 1 / sync,
        stab_pop = 1 / avg_cv_sp,
        ct_alive = map_dbl(max_int_alive,
          ~ifelse(sum(.x) == 0, 0,
            sum(.x > 0) / ((ncol(.x))^2))),
        bm_sp_alive = map(bm_sp, ~.x[.x > 10^-6]),
        tlvl_alive = map2(tlvl, bm_sp, ~.x[.y > 10^-6]),
        max_tlvl_alive = map_dbl(tlvl_alive, max),
        w_avg_tlvl_alive = map2_dbl(tlvl_alive, bm_sp_alive,
          ~sum(.x * (.y / sum(.y)))
          ),
        max_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) == 0, 0, max(.x[.x > 0]))
          ),
        avg_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) == 0, 0, mean(.x[.x > 0]))
          ),
        sd_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) <= 1, 0, sd(.x[.x > 0]))
          ),
        cv_max_int_alive = sd_max_int_alive / avg_max_int_alive,
        inv_sd_max_int_alive = 1 / sd_max_int_alive,
        gini_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) == 0, 0, gini(.x[.x > 0])))
      )
  )
)
```





```{targets sim_rho, tar_simple = TRUE}
simZ %>%
  filter(ct_alive != 0, avg_max_int_alive != 0) %>%
  mutate(across(c(async, sync, stab_pop, avg_cv_sp, stab_com, richness, avg_max_int_alive, gini_max_int), log, , .names = "log_{.col}")) %>%
  mutate(
    log1_avg_max_int_alive = log(avg_max_int_alive + 1),
    productivity_f = factor(productivity)
    ) %>%
  select(c(
      ct_alive, log_richness, max_tlvl_alive, Z, rho,
      gini_max_int, avg_max_int_alive, log1_avg_max_int_alive, env_stoch,
      log_stab_com, log_sync, log_async, log_stab_pop, log_avg_cv_sp, productivity, productivity_f,
      persistence)
  )
```

```{targets sim_rho_scaled, tar_simple = TRUE}
sim_rho %>%
  mutate(across(where(is.double), ~scale(.x)[,1]))
```

```{targets rho_model}
list(
  tar_target(formula_fixed_rho, "log_richness +
    ct_alive +
    log1_avg_max_int_alive +
    productivity +
    rho +
    I(rho^2) +
    env_stoch +

    log_richness:ct_alive +
    log_richness:log1_avg_max_int_alive +
    log_richness:productivity +
    log_richness:rho +

    log1_avg_max_int_alive:ct_alive +
    log1_avg_max_int_alive:productivity +
    log1_avg_max_int_alive:rho +

    ct_alive:rho +
    ct_alive:productivity +
    rho:productivity +
    I(rho^2):productivity +


    log_richness:log1_avg_max_int_alive:ct_alive +
    log_richness:log1_avg_max_int_alive:productivity +
    log_richness:log1_avg_max_int_alive:rho +
    log_richness:ct_alive:productivity +
    log_richness:ct_alive:rho +
    log_richness:rho:productivity +

    log1_avg_max_int_alive:ct_alive:rho +
    log1_avg_max_int_alive:ct_alive:productivity +
    log1_avg_max_int_alive:rho:productivity +

    ct_alive:rho:productivity"
    ),
  tar_target(formula_rand_rho, "(1 | Z)"),
  tar_target(mod_rho, map(setNames(
    c("log_stab_com", "log_stab_pop", "log_async"),
    c("log_stab_com", "log_stab_pop", "log_async")
    ),
  function (x) {
    glmmTMB(formula(paste0(x, " ~ ", formula_fixed_rho, " + ", formula_rand_rho)),
      sim_rho)
  }
  )),
  tar_target(coef_mod_rho, map_dfr(mod_rho, ~model2tibble(.x))),
  tar_target(r2_mod_rho, map_dfr(mod_rho, ~as.data.frame(r2_nakagawa(.x)), .id = "response") %>%
  mutate(response = var_replacement()[response])),
  tar_target(p_mod_rho, plot_effect_type(coef_mod_rho)),
  tar_target(mod_rho_scaled, map(setNames(
    c("log_stab_com", "log_stab_pop", "log_async"),
    c("log_stab_com", "log_stab_pop", "log_async")
    ),
  function (x) {
    glmmTMB(formula(paste0(x, " ~ ", formula_fixed_rho, " + ", formula_rand_rho)),
      sim_rho_scaled)
  }
)
    ),
  tar_target(coef_mod_rho_scaled, map_dfr(mod_rho_scaled, ~model2tibble(.x))),
  tar_target(r2_mod_rho_scaled,
    map_dfr(mod_rho_scaled, ~as.data.frame(r2_nakagawa(.x)), .id = "response") %>%
      mutate(response = var_replacement()[response])),
  tar_target(colin_rho, performance::check_collinearity(lm(formula(str_replace_all(paste0("log_stab_com ~ ", formula_fixed_rho), "(\\*|:)", "+")),
  sim_rho_scaled))),
    tar_target(p_mod_rho_scaled, plot_effect_type(coef_mod_rho_scaled))
)
```

```{targets pred_rho}
tar_target(pred_rho,
  {
  pred_rho <- list(
    log_richness = c(log(1), log(5), log(10), log(20), log(30), log(50)),
    ct_alive = c(.05, .10, .40),
    rho = c(0, .5, 1),
    log1_avg_max_int_alive = c(log(0.2 + 1), round(log(.81 + 1), 1), round(log(5.65 + 1), 1)),
    env_stoch = .5,
    productivity = c("basic", "enrichment"),
    Z = 100
    ) %>% expand.grid() %>%
  filter(
    !(log1_avg_max_int_alive == 0 & ct_alive != 0 | ct_alive == 0 & log1_avg_max_int_alive != 0)
  )
  pred_rho$log_stab_com <- predict(mod_rho[["log_stab_com"]], newdata = pred_rho)
  pred_rho
  }
)
```

# New simulation

```{targets raw_sim}
list(
tar_target(sim_fw_file, here::here("data", "sim_fw"), format = "file"),
  tar_target(sim_fw, readRDS(sim_fw_file)),
  tar_target(sim_fw_df, as.data.frame(sim_fw)),
  tar_target(sim_fw_cons, readRDS(here::here("data", "sim_fw_cons"))),
  tar_target(sim_fw_cons_df, as.data.frame(sim_fw_cons))
  )
```



## SEM

```{targets sem-process}
list(
  tar_target(sim_fw_sem,
    sim_fw_df %>%
      mutate(across(c(stab_com, pop_stab, async, cpe, sae_total, evenness_sae,
            sae_even, cpe_int, cpe_env), log))
    ),
  tar_target(sem_model_list,
    list(
      ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
      richness = lm(richness ~ ct + S, sim_fw_sem),
      #max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_sem),
      w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
      avg_omnivory = lm(avg_omnivory ~ ct + S, sim_fw_sem),
      avg_int_strength = lm(avg_int_strength ~ ct + S + h + Z, sim_fw_sem),
      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h + Z, sim_fw_sem),
      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + Z, sim_fw_sem),
      sae_even = lm(sae_even ~ richness, sim_fw_sem),
      cpe_int = lm(cpe_int ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + Z, sim_fw_sem),
      cpe_env = lm(cpe_env ~ richness + rho, sim_fw_sem),
      async = lm(async ~ sae_even + evenness_sae + cpe_env + cpe_int, sim_fw_sem),
      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
    )
    ),
  tar_target(sem, {
    ti <- as.psem(sem_model_list)
    update(ti, avg_omnivory %~~% w_avg_tlvl)
    }
    ),
  tar_target(sem_coeff, {
    ti <- summary(sem)$coefficients[, c(1, 2, 8, 9)]
    colnames(ti)[4] <- "Signif"
    ti #%>%
    #filter(abs(Std.Estimate) > 0.1)# %>%
    #  mutate(
    #    Response = var_replacement()[Response],
    #    Predictor = var_replacement()[Predictor]
    #  ) %>%
    }),
  tar_target(sim_eff_file, here::here("data", "sem_eff"), format = "file"),
  tar_target(sem_eff, {
    readRDS(sim_eff_file)
    #semEff(sem, ci.type = "perc", R = 10, seed = 13, parallel = "no", data = sim_fw_sem)
    }
    ),
  tar_target(sem_eff_tab, from_semEff_to_table(sem_eff)),
  tar_target(tab_sem_coeff,
    sem_coeff %>%
      kable(caption = "Standardized estimates for the Structural Equation Models.") %>%
      collapse_rows(1, valign = "middle") %>%
      kable_styling()
    ),
  tar_target(sem_collinearity,
    map_dfr(setNames(sem_model_list, names(sem_model_list)),
      performance::check_collinearity,
      .id = "response") %>%
    as_tibble),
  tar_target(sem_rsquared,
    map_dfr(sem_model_list, rsquared) %>%
      mutate(Response = var_replacement()[Response]) %>%
      select(Response, R.squared)
    ),
  tar_target(tab_sem_vif,
    sem_collinearity %>%
      mutate(
        response = var_replacement()[response],
        Term = var_replacement()[Term]
        ) %>%
      kable(
        caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
      kable_styling()
    ),
  tar_target(tab_sem_rsquared,
    sem_rsquared %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  )
)
```


# plot

```{targets p-stab}
list(
  tar_target(p_cpe_env_rho, sim_fw %>%
    ggplot(aes(x = as.factor(1 - rho), y = cpe_env)) +
    geom_hline(yintercept = 1, linetype = "dashed") +
    geom_hline(yintercept = .5, linetype = "dashed", color = "red") +
    geom_boxplot() +
    labs(x = "Response diversity", y = "Env. Compensatory effect") +
    theme_bw()),
  tar_target(p_stoch_pop_stab,
    sim_fw %>%
      ggplot(aes(x = as.factor(env_stoch), y = pop_stab)) +
      geom_boxplot() +
      labs(x = "Environmental stochasticity", y = "Population stability") +
      theme_bw()),
    tar_target(p_prod_bm,
      sim_fw %>%
        filter(bm_total > 10^-5) %>%
        ggplot(aes(x = as.factor(productivity), y = log(bm_total))) +
        geom_boxplot() +
        labs(x = "Productivity", y = "Total biomass") +
        theme_bw()
      ),
    tar_target(p_prod_pop_stab,
      sim_fw %>%
        ggplot(aes(x = as.factor(productivity), y = log(pop_stab))) +
        geom_boxplot() +
        labs(x = "Productivity", y = "Population stability") +
        theme_bw()
    ),
    tar_target(p_stab_comp_stress,
      plot_grid(
        p_cpe_env_rho,
        p_stoch_pop_stab,
        p_prod_bm,
        p_prod_pop_stab,
        labels = "auto"
      )

    )

)
```

## Stability-diversity relationship

```{targets p-stab-rich}
list(
#  tar_target(p_stab_s_prod,
#    sim_fw %>%
#      filter(productivity %in% c(5, 30), rho == 0, env_stoch == .3) %>%
#      ggplot(aes(x = richness, y = stab_com, color = as.factor(productivity))) +
#      geom_point() +
#      geom_smooth() +
#      labs(x = "Species richness", y = "Community stability", color = "Productivity") +
#      theme_bw()),
    tar_target(p_stab_s_env_stoch,
      sim_fw %>%
        filter(env_stoch %in% c(.5, 1.5), rho == 0) %>%
        ggplot(aes(x = richness, y = stab_com, color = as.factor(env_stoch))) +
        geom_point() +
        geom_smooth() +
        labs(x = "Species richness", y = "Community stability", color = "Env. variability") +
        theme_bw()),
      tar_target(p_stab_s_resp_div,
        sim_fw %>%
          filter(rho %in% c(0, 1), productivity == 5, env_stoch == .5) %>%
          ggplot(aes(x = richness, y = stab_com, color = as.factor(1 - rho))) +
          geom_point() +
          geom_smooth() +
          labs(x = "Species richness", y = "Community stability", color = "Response diversity") +
          theme_bw()
      ),
      tar_target(p_stab_s_stress,
         plot_grid(
#           p_stab_s_prod,
           p_stab_s_env_stoch,
           p_stab_s_resp_div,
           labels = "auto"
         )
      )
)
```

```{targets p_stab_rich_env_rho, tar_simple = TRUE}
sim_fw %>%
  filter(env_stoch %in% c(.1, .6), rho %in% c(0, .75), h == 3, Z == 100) %>%
  ggplot(aes(x = log(richness), y = log(stab_com), color = as.factor(rho))) +
  geom_point(alpha = .3) +
  geom_smooth(method = "lm") +
  facet_grid(cols = vars(env_stoch), labeller = label_both) +
  labs(
    x = "Species richness (Log)", y = "Community stability (Log)",
    color = "Environmental correlation"
  ) +
  theme_bw() +
  theme(legend.position = "bottom")
```


## Interaction strength effect

```{targets p_int_stab, tar_simple = TRUE}
sim_fw %>%
  filter(rho %in% c(0), productivity == 5, env_stoch == .5) %>%
  pivot_longer(c(stab_com, async, sae_total, cpe,
      sae_even, evenness_sae,
      cpe_int, cpe_env, stab_pop
      ), names_to = "async_decomp", values_to = "values") %>%
  mutate(async_decomp = var_replacement()[async_decomp]) %>%
  ggplot(aes(x = avg_int_strength, y = values)) +
  geom_point() +
  geom_smooth() +
  labs(x = "Avg feeding rate", y = "Asynchrony component") +
  facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
  theme_bw()
```

```{targets p_int_fw, tar_simple = TRUE}
sim_fw %>%
  filter(rho %in% c(0), productivity == 5, env_stoch == .5) %>%
  pivot_longer(c(richness, ct_alive, max_tlvl, avg_omnivory, w_avg_tlvl
      ), names_to = "fw_str", values_to = "values") %>%
  mutate(fw_str = var_replacement()[fw_str]) %>%
  ggplot(aes(x = avg_int_strength, y = values)) +
  geom_point() +
  geom_smooth() +
  labs(x = "Avg feeding rate", y = "Food-web structure") +
  facet_wrap(~fw_str, ncol = 3, scales = "free_y") +
  theme_bw()
```

## Avg Omnivory

```{targets p-omn}
list(
  tar_target(p_omn_stab,
    sim_fw %>%
      filter(rho %in% c(0), env_stoch == .5) %>%
      pivot_longer(c(stab_com, pop_stab, async
          ), names_to = "stab_comp", values_to = "values") %>%
      mutate(stab_comp = var_replacement()[stab_comp]) %>%
      ggplot(aes(x = avg_omnivory, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Avg omnivory", y = "Stability component") +
      facet_wrap(~stab_comp, ncol = 3, scales = "free_y") +
      theme_bw()),
  tar_target(p_omn_fw,
    sim_fw %>%
      filter(rho %in% c(0), env_stoch == .5) %>%
      pivot_longer(c(richness, ct_alive, w_avg_tlvl, max_tlvl
          ), names_to = "fw_str", values_to = "values") %>%
      mutate(fw_str = var_replacement()[fw_str]) %>%
      ggplot(aes(x = avg_omnivory, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Avg. Omnivory", y = "Food-web structure") +
      facet_wrap(~fw_str, ncol = 3, scales = "free_y") +
      theme_bw()
  )
)
```

```{targets p-ct-rich-stab}
list(
  tar_target(p_ct_stab,
    sim_fw %>%
      filter(rho %in% c(0), env_stoch == .1) %>%
      pivot_longer(c(stab_com, async, sae_total, cpe,
          sae_even, evenness_sae,
          cpe_int, cpe_env, stab_pop
          ), names_to = "async_decomp", values_to = "values") %>%
      mutate(async_decomp = var_replacement()[async_decomp]) %>%
      ggplot(aes(x = ct_alive, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Connectance", y = "Asynchrony component") +
      facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
      theme_bw()
    ),
  tar_target(p_rich_stab,
    sim_fw %>%
      filter(rho %in% c(0), env_stoch == .1) %>%
      pivot_longer(c(stab_com, async, sae_total, cpe,
          sae_even, evenness_sae,
          cpe_int, cpe_env, stab_pop
          ), names_to = "async_decomp", values_to = "values") %>%
      mutate(async_decomp = var_replacement()[async_decomp]) %>%
      ggplot(aes(x = richness, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Species richness", y = "Asynchrony component") +
      facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
      theme_bw()
    )
)
```

```{targets p_int_fw_str, tar_simple = TRUE}
p1 <- sim_fw %>%
  ggplot(aes(x = as.factor(richness), y = avg_int_strength)) +
  geom_point() +
  labs(x = "Species richness", y = "Avg. Interaction strength") +
  theme_bw()
p2 <- sim_fw %>%
  ggplot(aes(x = as.factor(Z), y = avg_int_strength)) +
  geom_boxplot() +
  labs(x = "PPBR", y = "Avg. Interaction strength") +
  theme_bw()
p3 <- sim_fw %>%
  filter(Z == 100) %>%
  ggplot(aes(x = as.factor(h), y = avg_int_strength)) +
  geom_boxplot() +
  labs(x = "Hill exponent", y = "Avg. Interaction strength") +
  theme_bw()
plot_grid(p1, p2, p3, ncol = 2)
```


```{targets p_cor, tar_simple = TRUE}
cor_var <- cor(
  sim_fw %>%
    select(c(richness, ct_alive, Z, bm_total,
        avg_int_strength, avg_omnivory, max_tlvl,
        w_avg_tlvl,
        rho, env_stoch, h,
        stab_com, pop_stab, async, sae_total, sae_even,
        evenness_sae, cpe, cpe_int, cpe_env)) %>%
  na.omit() %>%
  rename(any_of(get_rev_vec_name_val(var_replacement()))),
    method = "spearman")
ggcorrplot(cor_var, type = "lower", lab = TRUE)
```

```{targets p_sem_tot_stab, tar_simple=TRUE}
tar_read(sem_eff_tab) %>%
  filter(effect_type == "total") %>%
  filter(response %in% c("async", "pop_stab", "stab_com")) %>%
  filter(!predictor %in% c("evenness_sae", "sae_even", "cpe_int", "cpe_env", "pop_stab", "async")) %>%
  mutate(across(c(response, predictor), ~var_replacement()[.x])) %>%
  ggplot(aes(
      x = predictor,
      y = effect,
      ymin = lower_ci,
      ymax = upper_ci)
    ) +
  geom_pointrange() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  facet_grid(cols = vars(response)) +
  labs(x = "Predictor", y = "Total effect") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```


# Pipeline

If you ran all the `{targets}` chunks in non-interactive mode, then your R scripts are set up to run the pipeline.

```{r}
tar_make()
```

# Output

You can retrieve results from the `_targets/` data store using `tar_read()` or `tar_load()`.

```{r, message = FALSE}
library(targets)
library(tidyverse)
library(magrittr)
library(cowplot)
library(here)
library(arrow)
library(piecewiseSEM)
library(semEff)
library(easystats)
library(glmmTMB)
library(ggcorrplot)
source(here::here("R", "network_metrics.R"))
source(here::here("R", "string_replacements.R"))
source(here::here("R", "stability_decomposition.R"))
source(here::here("R", "model_helpers.R"))
```


```{r}
tar_load(sim_fw_df)
sim_fw_df %<>%
  mutate(across(c(stab_com, pop_stab, async, cpe, sae_total, evenness_sae, sae_even, cpe_int, cpe_env), log))

tu <- list(
      #ct_alive = lm(ct_alive ~ ct + S, sim_fw_df),
      #richness = lm(richness ~ ct + S, sim_fw_df),
      #  max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_df),
      w_avg_tlvl = lm(w_avg_tlvl ~ richness + ct_alive + Z, sim_fw_df),
      avg_omnivory = lm(avg_omnivory ~ ct_alive + richness, sim_fw_df),
      avg_int_strength = lm(avg_int_strength ~ ct_alive + richness + h, sim_fw_df),
      pop_stab = lm(pop_stab ~ Z + richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h, sim_fw_df),
      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive, sim_fw_df),
      sae_even = lm(sae_even ~ richness, sim_fw_df),
      cpe_int = lm(cpe_int ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h, sim_fw_df),
      cpe_env = lm(cpe_env ~ richness + rho, sim_fw_df),
      async = lm(async ~ sae_even + evenness_sae + cpe_env + cpe_int, sim_fw_df),
      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_df)
    )
map_dfr(tu, check_collinearity)
sem <- as.psem(tu)
sem <- update(sem, avg_omnivory %~~% w_avg_tlvl)
```

```{r}
ti <- compute_rotated_pca(sim_fw_df %>% select(
    richness, w_avg_tlvl, avg_omnivory, avg_int_strength,
    max_tlvl
    ), naxis = 2)
p <- plot_rotated_pca(pca_rotated = ti, axis = c(1, 2))
p[[1]]
```

```{r}
ti <- compute_rotated_pca(sim_fw_df %>% select(
    w_avg_tlvl, avg_omnivory, avg_int_strength
    ), naxis = 2)
p <- plot_rotated_pca(pca_rotated = ti, axis = c(1, 2))
p[[1]]
p$rotated
cor(ti$rotated$scores[, "RC1"], sim_fw_df[,"richness"])
```






```{r}
tar_load(c(sim_fw))
colnames(sim_fw)
summary(sim_fw$avg_int_strength)
unique(sim_fw$env_stoch)
tar_read(p_cor)
tar_read(p_prod_pop_stab)
tar_read(p_stab_s_stress)
tar_read(p_ct_stab)
tar_read(p_rich_stab)

sim_fw %>%
  filter(env_stoch == 0.3, rho %in% c(0, .5, 1), productivity == 5) %>%
  ggplot(aes(x = richness, y = cpe_env, color = as.factor(rho))) +
  geom_point() +
  labs(x = "Species richness", y = "Comp. effects (Environment)") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .6, rho == 0) %>%
  ggplot(aes(x = as.factor(productivity), y = pop_stab, color = as.factor(Z))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .3, rho == 0) %>%
  ggplot(aes(x = as.factor(productivity), y = stab_com, color = as.factor(Z))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .2, rho == 0) %>%
  ggplot(aes(x = as.factor(Z), y = pop_stab, color = as.factor(productivity))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .2, rho == 0) %>%
  ggplot(aes(x = as.factor(Z), y = avg_int_strength, color = as.factor(productivity))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .2, rho == 0, bm_total > 10^-5) %>%
  ggplot(aes(x = as.factor(Z), y = bm_total, color = as.factor(productivity))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .2, rho == 0) %>%
  ggplot(aes(x = as.factor(Z), y = evenness_sae, color = as.factor(productivity))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .2, rho == 0) %>%
  ggplot(aes(x = as.factor(productivity), y = cpe_int, color = as.factor(Z))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()
```

```{r}
var_fw_struct <- c("richness", "ct_alive", "Z")
var_fw_emergent_struct <- c("max_tlvl", "w_avg_tlvl", "avg_omnivory")
var_fw_flux <- c("avg_int_strength")
var_stab <- c("async", "stab_com", "pop_stab")
```

```{r, eval = FALSE}
#colnames(simZ)
pairs(sim_fw %>%
  filter(env_stoch == .2) %>%
  select(c(var_fw_struct, var_fw_emergent_struct, var_fw_flux, stab_pop)))
```

```{r}
unique(sim_fw$Z)
```

```{r}
sim_fw %>%
  filter(
    rho %in% c(0), productivity == 5, env_stoch == .5
    ) %>%
  ggplot(aes(y = stab_pop, x = as.factor(Z))) +
  geom_boxplot()
```



```{r}
sim_fw %>%
  filter(
    rho %in% c(0), productivity == 5, env_stoch == .5,
    Z == 500
    ) %>%
  pivot_longer(c(stab_com, async, sae_total, cpe,
      sae_even, evenness_sae,
      cpe_int, cpe_env, stab_pop
      ), names_to = "async_decomp", values_to = "values") %>%
  mutate(async_decomp = var_replacement()[async_decomp]) %>%
  ggplot(aes(x = as.factor(richness), y = values)) +
  geom_boxplot() +
  labs(x = "Connectance", y = "Asynchrony component") +
  facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
  theme_bw()
```

```{r}
tar_load(sim_sp)

sim_sp %>%
  filter(env_stoch == .3, rho == 1, Z == 100) %>%
  ggplot(aes(x = tlvl, y = log(cv_sp))) +
  geom_point() +
  geom_smooth()
```

```{r}
tar_read(sem_coeff) %>%
  filter(abs(Std.Estimate) > .1) %>%
  mutate(Std.Estimate = round(Std.Estimate, 1))
tar_read(sem_rsquared) %>%
  mutate(R.squared = round(R.squared, 2))
tar_load(sem_collinearity)
tar_read(sem_collinearity) %>%
  print(., n = 38)
```


```{r}
tar_load(c(sim_fw_sem, sim_fw))
mod_tot_scaled <- lm(stab_com ~
  richness + rho + env_stoch +
  ct_alive + avg_int_strength + w_avg_tlvl +
  richness : rho +
  richness : env_stoch +
  richness : ct_alive +
  richness : avg_int_strength +
  richness : w_avg_tlvl +
  richness : rho : ct_alive +
  richness : rho : w_avg_tlvl +
  richness : rho : avg_int_strength +
  richness : env_stoch : ct_alive +
  richness : env_stoch : w_avg_tlvl +
  richness : env_stoch : avg_int_strength,
sim_fw_sem %>%
  mutate(across(c("stab_com", "richness", "productivity", "rho", "env_stoch", "ct_alive", "avg_int_strength", "avg_omnivory", "w_avg_tlvl"), scale))

  )
summary(sim_fw$stab_com)
summary(sim_fw$avg_int_strength)
summary(sim_fw$w_avg_tlvl)
summary(sim_fw$avg_omnivory)

mod_tot <- lm(stab_com ~
  richness  + rho + env_stoch +
  ct_alive + w_avg_tlvl + Z +
  avg_int_strength +
  h +
  richness * rho +
  richness * env_stoch +
  richness * ct_alive +
  richness * avg_int_strength +
  richness * h +
  richness * w_avg_tlvl +
  richness * Z +
  richness * rho * ct_alive +
  richness * rho * w_avg_tlvl +
  richness * rho * avg_int_strength +
  richness * rho * h +
  richness * rho * Z +
  richness * env_stoch * ct_alive +
  richness * env_stoch * Z +
  richness * env_stoch * avg_int_strength+
  richness * env_stoch * h +
  richness * env_stoch * w_avg_tlvl,
  mutate(sim_fw, across(c(stab_com, richness), log)) #, richness
  )
check_collinearity(lm(stab_com ~ richness + rho +
    env_stoch + avg_int_strength +
  ct_alive + w_avg_tlvl + Z + h, sim_fw))
plot(mod_tot)

pred_data <- list(
  richness = log(seq(1, 30, 1)),
  ct_alive = c(.05, .10, .30),
  rho = c(0, .75, 1),
  avg_int_strength = c(.01, .02, .05, .1),
  env_stoch = c(.1, .3),
  w_avg_tlvl = c(1.5, 2, 3),
  Z = c(10, 100),
  h = c(2, 3)
  ) %>% expand.grid()
pred_data$stab_com <- predict(mod_tot, newdata = pred_data)
```

```{r}
p_pred_sr_int <- pred_data %>%
  filter(
    ct_alive %in% c(.1),
    rho %in% c(0, .75),
    Z == 10,
    h %in% c(3),
    avg_int_strength %in% c(.01, .05),
    w_avg_tlvl == 1.5
    ) %>%
  ggplot(aes(
      x = richness, y = stab_com,
      color = as.factor(rho),
      linetype = as.factor(avg_int_strength),
      )) +
  geom_line(linewidth = 2) +
  facet_grid(cols = vars(env_stoch), labeller = label_both) +
  labs(
    x = "Species richness (Log)", y = "Community stability (Log)",
    linetype = "Avg. Interaction strength",
    color = "Environmental correlation"
  ) +
  theme_bw() +
  theme(legend.position = "bottom")
ggsave(
  here("report", "figures", "p_pred_sr_int.png"),
  plot = p_pred_sr_int,
  scale = 2.4,
  width = 88,
  height = 88 * 1,
  units = "mm"
)
```

```{r}
plot_grid(
  tar_read(p_stab_rich_env_rho) + theme(legend.position = "none"),
  p_pred_sr_int)
```


```{r}

p_pred_sr_avg_tlvl_h <- pred_data %>%
  filter(
    ct_alive %in% c(.3),
    h %in% c(2,3),
    rho %in% c(0, 1),
    Z == 10,
    avg_int_strength %in% c(.1),
    w_avg_tlvl == c(1.5, 3)) %>%
  ggplot(aes(x = richness, y = stab_com, linewidth = as.factor(w_avg_tlvl), color = as.factor(h))) +
  geom_line() +
  facet_grid(cols = vars(env_stoch), rows = vars(rho), labeller = label_both) +
  theme_bw()
ggsave(
  here("report", "figures", "p_pred_sr_avg_tlvl_h.png"),
  plot = p_pred_sr_avg_tlvl,
  scale = 2.4,
  width = 88,
  height = 88 * 1,
  units = "mm"
)
```

```{r}
```





```{r}
tar_load(sem_eff_tab)
sem_eff_tab %>%
  filter(abs(effect) > .1) %>%
  filter(effect_type == "direct") %>%
  print(., n = 30)

```


```{r}
tar_load(sim_fw_sem)
sim_fw_sem %<>% mutate(richness = sqrt(richness))
ti <- as.psem(sem_model_list)
update(ti, avg_omnivory %~~% w_avg_tlvl)
sem_coeff <- summary(ti)$coefficients[, c(1, 2, 8, 9)]
map_dfr(sem_model_list, rsquared) %>%
      mutate(Response = var_replacement()[Response]) %>%
      select(Response, R.squared)
```

```{r}
sem_model_list <- list(
      ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
      richness = lm(richness ~ ct + S, sim_fw_sem),
      #max_tlvl = lm(max_tlvl ~ ct + S, sim_fw_sem),
      #w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
      #avg_omnivory = lm(avg_omnivory ~ ct + S, sim_fw_sem),
      avg_int_strength = lm(avg_int_strength ~ ct + S + h + Z, sim_fw_sem),
      pop_stab = lm(pop_stab ~ richness + avg_int_strength + ct_alive + env_stoch, sim_fw_sem),
      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + ct_alive, sim_fw_sem),
      sae_even = lm(sae_even ~ richness, sim_fw_sem),
      cpe_int = lm(cpe_int ~ richness + avg_int_strength + ct_alive, sim_fw_sem),
      cpe_env = lm(cpe_env ~ richness + rho, sim_fw_sem),
      async = lm(async ~ sae_even + evenness_sae + cpe_env + cpe_int, sim_fw_sem),
      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
    )
ti <- as.psem(sem_model_list)
update(ti, avg_omnivory %~~% w_avg_tlvl)
sem_coeff <- summary(ti)$coefficients[, c(1, 2, 8, 9)]
map_dfr(sem_model_list, rsquared) %>%
      mutate(Response = var_replacement()[Response]) %>%
      select(Response, R.squared)
```








The `targets` dependency graph helps your readers understand the steps of your pipeline at a high level.

```{r}
tar_visnetwork()
```

At this point, you can go back and run `{targets}` chunks in interactive mode without interfering with the code or data of the non-interactive pipeline.
