---
title: "Interaction strength: driven by metabolism or behavior? McCann vs Brose" 
author: Alain Danet
date: \today
output:
  bookdown::html_document2:
    fig_caption: true 
    toc: true
    fontsize: 12pt
    number_sections: true
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE,
  fig.path="figures/"
)
```

```{r}
library(tidyverse)
library(magrittr)
library(plotly)
library(kableExtra)
library(cowplot)
```

```{r}
theme_set(theme_half_open() + background_grid())
```


```{r}
# From McCann diamond
x <- c(0, .40, .20, .08)
y <- c(0, 2.009, 3.50, 5.0)
b0 <- c(0.16129, .90, .5)
names(x) <- names(y) <- c("R1", "C1", "C2", "P")
names(b0) <- c("R01", "R02", "C0")
```

# Context

Brose's and McCann's body of work represent two different ways of seeing foodweb
assembly and dynamics. McCann considers that foodwebs are made of strong
interactions that are stabilized by weak interactions. A consequence of this is
that the asymmetry in consumer preference for resources plays a great role in
McCann's work ($\omega$), where the predator has a preference for the most
competitive prey (hierarchy mostly defined by the asymmetry in half saturation
constant $B_0$). We can see it as a strong role given to consumer preference as
a predominant role of foraging behavior in McCann work. This approach leads to
the construction of small and finely tuned foodweb module, up to four species
(one producer, two consumers and one predator).

In contrast, Brose's body of work does not make assumption on foraging behavior
and so on asymmetry of consumer preference. Furthermore, it does not assume
competitive difference between consumers for resources (same half-saturation
constants). In Brose's work, the interaction strength are only determined by the
trophic level and a constant body size ratio ($Z$ parameter) between pairs of
adjacent trophic levels. At the end, interaction strengths are solely determined
by metabolism, through body mass, which determines in turn maximum ingestion and
metabolism rates. In contrast with McCann approach, it enables to build
species-rich foodweb without having to finely tune each parameter, as the
metabolic parameters and interactions are (almost) solely determined by the body
mass ratio ($Z$) and the trophic level (T). This convenient parametrization of
complex food-webs has the cons to consider that there is no behavior or
competitive hierarchy in the food-web, all is solely determined by metabolism.

In a nutshell, McCann proposes that the balance of strong and weak interactions
driven by consumer preference and competitive hierarchy drive the stability of
foodweb while Brose proposes that stability emerge from weak interactions driven
by the slow metabolism of predators compared to the preys (high Z).

In this document, I try to derive the relationship among maximum interaction
strength, body mass ratio and consumer preferences to map the range of
interactions strength explored by Brose. I then map the McCann interaction
strength onto it by computing the body mass ratio (Z) between consumers and
predator. I finally try to estimate what would be the body mass ratio between
consumer and predator to mimic the interaction strength of McCann without
predator preference for any of the two consumers (i.e. $\omega = .5$).
 
# Maximum interaction strength from McCann 

```{r}
max_int <- function(
  omega = .5,
  ax = 0.88,
  y = 5,
  x = NULL,
  ay = NULL,
  Z = 1,
  T = 2,
  b0 = 0.50) {

  if (is.null(ay) & !is.null(ax)) {
    ay <- ax * y
  }

  if (!is.null(Z)) {
    numerator <- omega * ax * ay * Z ^ ((T - 1) * (-0.5))
  } else {
    numerator <- omega * x * y
  }
  numerator / b0
}
```

From McCann, maximum interaction strength ($I_{ki}$) is equal to: 

$$
I_{ki} = \dfrac{\omega_{ki} x_i y_i}{B_{0i}}
$$

```{r}
Imccann02_met <- max_int(omega = .02, y = y["P"], x = x["P"], ax = NULL, Z =
  NULL, T = 3, b0 = b0["C0"])
Imccann98_met <- max_int(omega = .98, ax = NULL, y = y["P"], x = x["P"], ay =
  NULL, Z = NULL, T = 3, b0 = b0["C0"])

ImccannC1R_met <- max_int(omega = 1, ax = NULL, y = y["C1"], x = x["C1"], ay =
  NULL, Z = NULL, T = 2, b0 = b0["R01"])

ImccannC2R_met <- max_int(omega = 1, ax = NULL, y = y["C2"], x = x["C2"], ay =
  NULL, Z = NULL, T = 2, b0 = b0["R02"])
```

```{r}
interaction_correspondance <- tibble(
  int = c("P-C1", "P-C2", "C1-R", "C2-R"),
  omega = c(.98, .02, 1, 1),
  I = map_dbl(c(Imccann98_met, Imccann02_met, ImccannC1R_met, ImccannC2R_met),
    ~round(.x, 2))
)
interaction_correspondance %>%
  kbl(
    caption = "Interaction strength from McCann 1998",
    label = "int"
  ) %>%
kable_styling()
```

From the first equation, we can compute $I$ of McCann from the metabolic rates,
giving interaction strengths presented in Table \@ref(tab:int).

From The formulation of $I$, we can compute $I(Z)$ if we replace $x_i$ and $y_i$ by $Z$.  

Knowing that $x_i = a_xM_i^{-0.25}$, $y_i = a_yM_i^{-0.25}$ and that $M =
Z^{T-1}$, we can derive that: $x_i = a_x(Z^{T-1})^{-0.25}$

\begin{align}
I_{ki} &= \dfrac{\omega_{ki} a_x(Z^{T-1})^{-0.25} a_y(Z^{T-1})^{-0.25}}{B_{0i}} \\

I_{ki} &= \dfrac{\omega_{ki} a_x a_y ((Z^{T-1})^2)^{-0.25} }{B_{0i}} \\

I_{ki} &= \dfrac{\omega_{ki} a_x a_y (Z^{T-1})^{-0.5} }{B_{0i}} \\

I_{ki} &= \dfrac{\omega_{ki} a_x a_y Z^{-(T-1)/2}}{B_{0i}} \\

I_{ki} &= \dfrac{\omega_{ki} a_x a_y Z^{-(T-1)/2}}{B_{0i}}
\end{align}

Then we can compute maximum interaction strength from $Z$, $\omega$ and
$B_{0i}$.

```{r}
# Prepare Z and omega combination
comb_list <- list(
  Z = purrr::map_dbl(seq(-2, 5, .05), ~10^.x),
  omega = seq(0, 1, .05)
)
# Compute maximum interaction strength
result <- comb_list %>%
  expand.grid() %>%
  as_tibble() %>%
  mutate(
    I = map2_dbl(omega, Z, ~max_int(omega = .x, Z = .y, y = y["P"], T = 3))
  )

result_lg <- result %>%
  pivot_wider(names_from = "omega", values_from = "I")
res_mat <- as.matrix(result_lg[, -1])
row.names(res_mat) <- result_lg$Z

fig <- plot_ly(
  # Omega
  x = as.numeric(colnames(res_mat)),
  # Z 
  y = as.numeric(rownames(res_mat)),
  # I
  z = res_mat) %>%
  add_surface() %>%
  layout(
    title = "For predator of trophic level = 3",
    scene = list(
      xaxis = list(title = "Consumer preference"),
      yaxis = list(type = "log", title = "Z"),
      zaxis = list(title = "Maximum interaction strength")
    )
  )
```

```{r}
# Compute Z from McCann int strength taking in account omega 
z_from_int <- function(
  I = .48,
  b0 = .5,
  omega = .5,
  ax = .88,
  y = 5,
  T = 2
  ) {
  ay <- ax * y
  ((I * b0) / (omega * ax * ay)) ^ (- 2 / (T - 1))
}

Zmccann <- z_from_int(I = Imccann02_met, omega = .02, T = 3)
Zmccann <- z_from_int(I = Imccann98_met, omega = .98, T = 3)

ZmcannC1 <- z_from_int(I = ImccannC1R_met, omega = 1, T = 2)
ZmcannC2 <- z_from_int(I = ImccannC2R_met, omega = 1, T = 2)
```



```{r}
fig2 <- fig %>%
  add_markers(
    # Omega
    x = c(.02, .98),
    # Z
    y = c(Zmccann, Zmccann),
    # I
    z = c(Imccann02_met, Imccann98_met),
    color = I("blue")
    )
```

```{r}
Zbrose_int02 <- z_from_int(I = Imccann02_met, omega = .5, T = 3)
Zbrose_int98 <- z_from_int(I = Imccann98_met, omega = .5, T = 3)
```

```{r}
interaction_correspondance$Z <- c(Zmccann, Zmccann, ZmcannC1, ZmcannC2)
interaction_correspondance %>%
  kbl(
    caption = "Interaction strength from McCann 1998 and their corresponding
    translation in Z",
    label = "intZ"
  ) %>%
kable_styling()
```

We can then compute $Z$ from $I$ and $\omega$ such as

\begin{align}
Z^{-\dfrac{T-1}{2}} &= \dfrac{I_{ki} B_{0i}}{\omega a_x a_y} \\

Z &= \dfrac{I_{ki} B_{0i}}{\omega a_x a_y}^{-\dfrac{2}{T-1}}
\end{align}

It gives us what is the $Z$ equivalent of interaction strengths in McCann. We
can then plot the interaction of McCann in Brose framework (In blue, Fig.
\@ref(fig:intzomega)). We can furthermore infer what would be the equivalent of
McCann in Brose framework, i.e. with $\omega = .5$, i.e. in case that there are no
consumer preference. We found that the weak interaction (P-C2) would correspond
to $Z = `r Zbrose_int02`$ and the strong interaction (P-C1) to
$Z = `r Zbrose_int98`$ in Brose framework.

```{r}
intzomega_cap <- "Maximum interaction strength between a predator and consumer
of T = 3 and T = 2 according to Z and omega (range corresponding to Brose et al.
  2006). In blue are mapped the values corresponding to McCann P/C1 and P/C2
interactions. In red are mapped the values corresponding to McCann P/C1 and
P/C2, but in case where there is no consumer preference (Brose's framework)."
```


```{r intzomega, fig.cap=intzomega_cap}
fig2 %>%
  add_markers(
    # Omega
    x = c(.5, .5),
    # Z
    y = c(Zbrose_int02, Zbrose_int98),
    # I
    z = c(Imccann02_met, Imccann98_met),
    color = I("red"),
    labels = c("test", "test2")
    )
```


# Example of simulations


```{r}
species_replacement <- c("R", "C1", "C2", "P")
names(species_replacement) <- paste0("value", seq(1,4)) 
```

```{r}
mccann_origin <- read_csv("mcann_original.csv")
p_mccann_origin <- mccann_origin %>%
  pivot_longer(-timestamp, names_to = "species", values_to = "bm") %>%
  mutate(species = species_replacement[species]) %>%
  ggplot(aes(x = timestamp, y = bm, color = species)) +
  geom_line() +
  labs(x = "Time", y = "Biomass")

leg <- get_legend(p_mccann_origin + theme(legend.position = "bottom"))
```

```{r}
mccann_z <- read_csv("mcann_z.csv")
p_mccann_z <- mccann_z %>%
  pivot_longer(-timestamp, names_to = "species", values_to = "bm") %>%
  ggplot(aes(x = timestamp, y = bm, color = species)) +
  geom_line()+
  labs(x = "Time", y = "Biomass", color = "Species")
```

```{r}
brose_little_z <- read_csv("brose_little_z.csv")
p_brose_little_z <- brose_little_z %>%
  pivot_longer(-timestamp, names_to = "species", values_to = "bm") %>%
  ggplot(aes(x = timestamp, y = bm, color = species)) +
  geom_line() +
  labs(x = "Time", y = "Biomass")
```

```{r}
brose_big_z <- read_csv("brose_big_z.csv")
p_brose_big_z <- brose_big_z %>%
  pivot_longer(-timestamp, names_to = "species", values_to = "bm") %>%
  ggplot(aes(x = timestamp, y = bm, color = species)) +
  geom_line() +
  labs(x = "Time", y = "Biomass")
```

```{r}
sim_cap <- paste0("Simulation of the bioenergetic model for four simulations. (a)
  Original McCann model. (b) McCann model but metabolic rates have been
  drawn from the inferred Z between Predator and consumers (Z = ", Zmccann ,"), but
  does not consider that Z might be different for Predator/Consumer and
  Consumer/Resource. So, here everything crashes because interactions P/C might be
  too strong compared to C/R interactions. (c) Brose model with Z corresponding to
  the strong interaction P/C1. (d) Brose model with Z corresponding to the weak interaction P/C2.") 

```


```{r sim, fig.cap=sim_cap}
top <- plot_grid(
  p_mccann_origin + theme(legend.position = "none"),
  p_mccann_z + theme(legend.position = "none"),
  p_brose_little_z + theme(legend.position = "none"),
  p_brose_big_z + theme(legend.position = "none"),
  ncol = 2,
  labels = "auto")
plot_grid(top, leg, nrow = 2, rel_heights = c(1, .1))
```


# Calculus trash

If you compute two Z (useless): 

$$
I_{ki} = \dfrac{\omega_{ki} a_x a_y (Z^{T-1} Z^{T-1})^{-0.25} }{B_{0i}}
$$

You can also compute Z from metabolic parameters:

$Z_x^{T-1} = \dfrac{x_i}{a_x}$

$Z_x = (\dfrac{x_i}{a_x})^(1 / (T-1))$ because $(Z^{T-1})^{1/ (T-1)} = Z$

and 

$Z_y = (\dfrac{y_i}{a_y})^(1 / (T - 1))$

Finally, from above equation, $Z = Z_x Z_y$

```{r}
z_from_y_x <- function(ax = .88, x = .08, y = 5, T = 3) {
  ay <- ax * y
  c(
    Zy = (y / ay) ^ (1 / (T - 1)),
    Zx = (x / ax) ^ (1 / (T - 1))
  )
}

# Z infered from parameters of McCann et al. 1998 and Vasseur and Fox
Zmccann <- Reduce(`*`, z_from_y_x(ax = .88, x = x["P"], y = y["P"], T = 2))
ZC1mccann <- Reduce(`*`, z_from_y_x(ax = .88, x = x["C1"], y = y["C1"], T = 2))
ZC2mccann <- Reduce(`*`, z_from_y_x(ax = .88, x = x["C2"], y = y["C2"], T = 2))
```
