---
title: Response diversity is a major driver of temporal stability in complex food webs
author: ""
date: ""
output:
  officedown::rdocx_document:
    number_sections: false
    base_format: "bookdown::word_document2"
  bookdown::pdf_document2:
    keep_tex: true
    latex_engine: xelatex
    spacing: double
    number_sections: false
always_allow_html: true
bibliography: references.bib
link-citations: true
csl: proceedings-of-the-royal-society-b.csl
toc: false
linestretch: 2.0
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{hyperref}
  - \hypersetup{backref=true}
  - \usepackage{setspace}\doublespacing
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.pos = "H",  # pdf mode
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE,
  fig.path="figures/"
)
```

```{r, results = FALSE}
sapply(c("targets", "tidyverse", "magrittr", "cowplot", "here", "piecewiseSEM",
    "semEff", "ggcorrplot", "kableExtra", "rmarkdown", "officedown"),
  require,
  character.only = TRUE)
mytheme <- theme_cowplot(font_size = 8) +
background_grid() +
theme(legend.position = "bottom")
theme_set(mytheme)
sapply(list.files(here("R"), full.names = TRUE), source)
```

\pagebreak

# Abstract

Global change constitutes a major threat to biodiversity and ecosystem
functioning and places the temporal stability of ecological communities at risk.
Food web structure and species richness have been identified in classic theory
as critical drivers of temporal stability, however, recent theory centred on
response diversity and stochasticity integrates new ways of altering
stability. Using a stochastic, bioenergenetic food web model, we integrate these
multiple bodies of theory to reveal that response diversity is a major driver of
community stability. Moreover, our integrated theory reveals a novel insight
that positive stability-richness relationships emerge only in the presence of
response diversity. In contrast to previous work, we also find that food web
structure is only a secondary driver of community stability, but interacts with
response diversity to determine the sign of the stability-richness relationship.
Our study reveals identifiable pathways by which food web structure and response
diversity drive community stability, and raises concerns about how the loss of
response diversity (biotic homogenisation) may lead to a breakdown of community
stability.

\pagebreak

# Introduction

The response of ecological communities to environmental perturbations has long
been a central research topic  in ecology [@macarthur_fluctuations_1955;
@may_will_1972]. A robust body of empirical and theoretical work has
demonstrated that species diversity can buffer the effects of such
perturbations, enhancing the temporal stability of communities. This stabilizing
effect has been observed in competitive assemblages [@yachi_biodiversity_1999;
@doak_statistical_1998; @tilman_ecological_1999; @de_mazancourt_predicting_2013;
@thibaut_diversity_2012; @zhao_biodiversity_2022] and bi-trophic systems, such
as plant-herbivore communities [@downing_ecosystem_2002;
@srednick_understanding_2024; @thebault_stability_2010].Current theory
highlights that these patterns of community stability arise via a set of three
interrelated processes: 1) Average population-level stability, which measures
the average temporal variability of individual species, 2) Asynchrony measures
the offset of population fluctuations at the community level
[@thibaut_understanding_2013; @zhao_biodiversity_2022]. Asynchrony is driven by
response diversity, i.e. the diversity of species' responses to environmental
fluctuations [@elmqvist_response_2003; @sasaki_species_2019; @ross_how_2023;
@polazzo_measuring_2024] which can result in either compensatory dynamics among
species due environmental fluctuations, or statistical averaging [i.e. portfolio
effects, @doak_statistical_1998; @thibaut_understanding_2013;
@zhao_biodiversity_2022] in the special case where species have effectively
independent responses to environmental perturbations. Species interactions can
also generate compensatory dynamics and thereby constitute another source of
asynchrony [@mccann_reevaluating_1997; @mccann_weak_1998; @ives_stability_2000;
@thebault_trophic_2005; @thebault_relationship_2006; @zhao_biodiversity_2022].
3) Species richness and food web structure such as trophic levels and
interaction strength modulate the above processes [@may_will_1972;
@angelis_stability_1975; @mccann_weak_1998; @mccann_reevaluating_1997;
@thebault_trophic_2005; @thebault_relationship_2006; @thebault_stability_2010].
Critically, these processes are deeply interconnected. For instance, response
diversity to environmental perturbations may increase asynchrony
[@thibaut_diversity_2012; @thibaut_understanding_2013; @sasaki_species_2019],
but food web structure can synchronise species via trophic interactions
[@raimondo_interspecific_2004; @korpimaki_predatorinduced_2005;
@mccann_weak_1998; @mccann_diversitystability_2000;
@fahimipour_compensation_2017]. Yet their relative contributions to community
stability remain poorly understood, particularly in complex, multi-trophic
systems. Here, we first review and synthesize these processes. We then introduce
a modeling approach and in-silico experiment to disentangle their effects,
ultimately delivering novel insights about when and how species richness and
food web structure enhance or impair community stability.

Temporal stability in ecological communities can be decomposed into two key
components: average population stability (hereafter “population stability”) and
asynchrony [@thibaut_understanding_2013; @zhao_biodiversity_2022]. Population
stability reflects the variability of individual species quantities over time
(e.g. abundance or biomass), while asynchrony captures the degree to which
fluctuations in different species offset one another. Previous theoretical and
empirical studies highlighted that population stability decreases strongly with
environmental stochasticity and that it can decrease, increase, or do not change
with increasing species richness [@tilman_biodiversity_2006;
@loreau_biodiversity_2013; @houlahan_negative_2018]. Food web
structure—including trophic levels, interaction strengths, and connectance—plays
a critical role in mediating community stability [@may_will_1972;
@angelis_stability_1975; @mccann_weak_1998; @mccann_reevaluating_1997;
@ives_stability_2000; @thebault_trophic_2005; @thebault_relationship_2006;
@eschenbrenner_diversity_2023]. For instance, the presence of higher trophic
levels can increase population stability [@brose_allometric_2006;
@shanafelt_stability_2018; @danet_species_2021; @eschenbrenner_diversity_2023]
because of their lower natural mortality rates [@brose_allometric_2006;
@hatton_linking_2019] or their top-down control on other species
[@shanafelt_stability_2018]. Strong trophic interactions and higher connectance
tend to reduce population stability [@may_will_1972; @mccann_reevaluating_1997;
@mccann_weak_1998; @thebault_trophic_2005].

Asynchrony comes into play when considering how species fluctuations offset each
other, thereby contributing to temporal stability at the community level
[@loreau_species_2008; @thibaut_understanding_2013; @zhao_biodiversity_2022].
In the absence of strong demographic stochasticity [@loreau_species_2008;
@loreau_biodiversity_2013], asynchrony stems from two origins: (i) response
diversity to environmental perturbations or (ii) species interactions. Species'
response diversity to enviromental perturbations which lead to either
statistical averaging and strong portfolio effects in the special case where
species' response are independant [@doak_statistical_1998] or compensatory
dynamics among species due to the structure of response diversity
[@zhao_biodiversity_2022]. These processes have been
well-documented in single-trophic systems, such as grasslands and bird
communities, where response diversity—variation in species’ responses to
environmental change—plays a critical role in driving asynchrony and stabilizing
communities [@yachi_biodiversity_1999; @thibaut_diversity_2012;
@thibaut_understanding_2013; @de_mazancourt_predicting_2013;
@olivier_urbanization_2020; @zhao_biodiversity_2022].

Response diversity arises from differences in species’ niches and environmental
preferences, leading to varied reactions to the same environmental perturbations
[@elmqvist_response_2003; @ross_how_2023]. For example, within a community, some
species may increase in abundance under warmer conditions while others decline,
depending on their thermal tolerances [@frund_response_2013]. This diversity of
responses buffers communities against environmental perturbations by increasing
asynchrony, enhancing stability [@yachi_biodiversity_1999;
@thibaut_diversity_2012; @thibaut_understanding_2013]. Indeed, using a
trait-based or a non trait-based approach, previous studies showed that response
diversity increases asynchrony [@thibaut_diversity_2012;
@thibaut_understanding_2013; @sasaki_species_2019]. Originally defined as the
diversity of species responses within functional groups
[@elmqvist_response_2003], the role of response diversity in multi-trophic
systems remains poorly understood, as trophic interactions can either amplify or
dampen its effects [@raimondo_interspecific_2004;
@korpimaki_predatorinduced_2005; @mccann_weak_1998;
@mccann_diversitystability_2000; @fahimipour_compensation_2017].

Trophic interactions, embedded in a food web structure, affect in turn
asynchrony through compensatory dynamics steming from species interactions.
While theory suggests that trophic interactions can alter the effects of
response diversity on asynchrony, either synchronizing prey dynamics through
top-down control [@raimondo_interspecific_2004; @korpimaki_predatorinduced_2005]
or enhancing compensatory dynamics via prey switching and trophic cascades
[@mccann_weak_1998; @mccann_diversitystability_2000;
@fahimipour_compensation_2017], their full integration in complex, multi-trophic
communities remains a significant gap in our understanding [@danet_species_2021;
@eschenbrenner_diversity_2023; @yang_predictability_2019]. These food web
structures also influence stability-richness relationships, where  for example,
species-rich communities often contain more trophic levels, making it
challenging to disentangle the effects of richness from those of food web
structure [@thebault_trophic_2005; @danet_species_2021;
@eschenbrenner_diversity_2023]. This complicates efforts to isolate the effects
of species richness per se [@dunne_network_2006; @galiana_spatial_2018].

Food web structure—including trophic levels, interaction strengths, and
connectance—plays a critical role in mediating asynchrony and thereby community
stability [@may_will_1972; @angelis_stability_1975; @mccann_weak_1998;
@mccann_reevaluating_1997; @ives_stability_2000; @thebault_trophic_2005;
@thebault_relationship_2006; @danet_species_2021;
@eschenbrenner_diversity_2023]. While most of the processes and patterns
described above have been well-studied in single-trophic systems, there remain
few efforts to extend beyond this. In the following sections, we integrate these
sets of processes by modifying and extending a bioenergetic food web
model [@brose_allometric_2006; @yodzis_body_1992] to incorporate environmental
stochasticity and response diversity [@vasseur_environmental_2007;
@ives_stability_2007; @ripa_food_2003]. We apply this model to over 45,000
in-silico communities with varying levels of species richness, trophic
complexity, connectance, and we experimentally manipulated interaction
strengths, response diversity, and environmental stochasticity. This in-silico
experiment allowed us to evaluate whether response diversity, species richness,
and food web structure act additively or interactively to drive community
stability, and under what conditions these factors lead to positive or negative
stability-richness relationships. Finally, using a Structural Equation Model and
linear models, we then tested how both the factors linked to environmental
fluctuations and their buffering (environmental stochasticity and response
diversity), and the ones mediating them (species richness and food web
structure) affect the components of community stability (population stability
and asynchrony).


```{r}
tar_load(sim_param_tab)
p_mm <- function(
  v = "S",
  data = sim_param_tab
) {
  out <- data[data$Parameter %in% v, ]
  paste0("", signif(out[["min"]], 1), "-", signif(out[["max"]], 1), "")
}
```

```{r, eval = FALSE}
p_mm("ct")
```

# Methods

## Bioenergenetic model

We simulated the dynamics of complex food webs using the allometric bioenergetic
model [@yodzis_body_1992; @rooney_homage_2006; @brose_allometric_2006;
@lajaaiti_ecologicalnetworksdynamicsjl_nodate]. This model is widely used to
simulate the dynamics of complex ecological communities because of the
simplicity of its parametrisation, where metabolic parameters are set based on
species body mass and metabolic types using the metabolic theory of ecology
[@brown_toward_2004]. The model describes species biomass ($B_i$) dynamics over time
of the primary producers ($B_{i \in \{\mathrm{prod.}\}}$, eq. \@ref(eq:prod)) and
the consumers ($B_{i \in \{\mathrm{cons.}\}}$, eq.\@ref(eq:cons)):

\begin{equation}
    (\#eq:cons)
        \frac{dB_{i \in \{\mathrm{cons.}\}}}{dt} =
        \sum_{j \in \{\mathrm{res.}\}_i} x_i y_i B_i F_{ij}
        - \sum_{j \in \{\mathrm{cons.}\}_i} \frac{x_j y_j B_j F_{ji}}{e_{ij}}
        - x_i B_i - d_i B_i
\end{equation}

\begin{equation}
    (\#eq:prod)
	\frac{dB_{i \in \{\mathrm{prod.}\}}}{dt} =
    r_i B_i G_i
    - \sum_{j \in \{\mathrm{cons.}\}_i} \frac{x_j y_j B_j F_{ji}}{e_{ij}}
    - d_i B_i
\end{equation}

The consumers gain biomass by consuming their resources, where $j \in\{\mathrm{res.}\}_i$
are the resources of the consumer $i$, at a rate
that depends on their metabolic rate ($x_i$), maximum consumption
rate ($y_i$) and on the functional response ($F_{ij}$) describing how the rate
of consumption of a consumer $i$ on one of its resources $j$ vary with the biomass of this
resource. The consumer metabolic rate was derived from ectotherm mass specific
metabolic rate ($a_x = 0.88$, Table S1) and species body masses ($M_i$):
$x_i=a_xM_i^b$, with $b=-1/4$ as defined in the allometric theory of metabolism
[@brown_toward_2004; @brose_allometric_2006].

Species then lose biomass by being consumed, where $j \in \{\mathrm{cons.}\}_i$
are the consumers of the species $i$, $e_{ij}$ is the assimilation efficiency
of the consumer $j$ on the resource $i$ [@rooney_homage_2006;
@brose_allometric_2006; @lajaaiti_ecologicalnetworksdynamicsjl_nodate].
Consumers also lose biomass over time through metabolic losses ($-x_iB_i$) and
natural mortality ($-d_iB_i$). The primary producers gain biomass over time with
a growth rate ($r_i$, eq. \@ref(eq:prod)) and a functional response ($G_i$)
describing how the growth of the producers vary with their biomass. They lose
biomass by being consumed by consumers and by natural mortality.

The growth of the primary producers (eq. \@ref(eq:growth)) is logistic,

\begin{equation}
    (\#eq:growth)
    G_i = (1 - \dfrac{\sum_{j \in \{\mathrm{prod.}\}} \alpha_{ij} B_j}{K_i})
\end{equation}

where the growth rate is maximal when $\sum_{j \in \{\mathrm{prod.}\}}
\alpha_{ij} B_j$ approaches $0$ and null when it approaches $K_i$. $\alpha_{ij}$ is the per
capita effect of the producer $j$ on the producer $i$, $K_i$ is the carrying
capacity for the producer $j$. The feeding rates of a consumer feeding on
a resource (eq. \@ref(eq:holling)) is described by a functional response,

\begin{equation}
    (\#eq:holling)
    F_{ij} = \frac{\omega_{ij} B_j^h}
    {B_0^h + c_i B_i
    	+ \sum_{k \in \{\mathrm{res.}\}_i} \omega_{ik} B_k^h}
\end{equation}

which depends on the relative preference of the consumer on the resource
($\omega_{ij}$) is limited by a half-saturation rate ($B_0$), intraspecific
interference coefficient ($c_i$), and on the availability of its other resources
($\sum_{k \in \{\mathrm{res.}\}_i} \omega_{ik} B_k^h$). Finally, the $h$
exponent controls the shape of the functional response from a saturating
function ($h = 1$, Holling type II) to a sigmoid ($h = 2$, Holling type III).

## Environmental stochasticity and response diversity

We added a stochastic natural mortality rate to the species dynamics,
representing a fluctuating environment. Based on the literature and previous
models [@vasseur_environmental_2007; @hatton_linking_2019], we assumed that natural mortality rates
scales inversely with the species body mass ($d_i = d_0M_i^{-1/4}$), as all
other physiological parameters. We used a basal natural mortality rate of $d_0 =
0.4$, as a previous study [@vasseur_environmental_2007].

We introduced environmental stochasticity by considering stochastic variation in
mortality rates. Doing so allows to consider stochasticity without modifying
species interactions themselves [@vasseur_environmental_2007]. The stochastic
part of the mortality rates ($\epsilon_{i, t}$) follow a normal distribution 0
centered ($\epsilon_{i, t} \sim N(0,\sigma^2_e)$) with a variance
($\sigma^2_e$). The mortality rates of each species at the time $t$ equals to
$d_{i,t} = d_i e^{\epsilon_{i, t}}$, which ensured that the mortality rates
never become negative [@vasseur_environmental_2007]. We simulated $\epsilon$ in
two steps: we first simulated a temporally correlated Ornstein-Uhlenbeck process
to generate the stochastic part of species mortality rates ($a_{i, t}$) and then
we multiplied those values by a correlation matrix to control the level of
response diversity. The Ornstein-Uhlenbeck process is a modified Brownian motion
where the stochastic values tend to come back to the central value (i.e. $a_i =
0$) such as $a_{i, t}$ varies according to this stochastic differential
equation: $da_{i} = (0 - a_i)d_t + \sigma_e dW_i$, where $dW_i$ is a Brownian
motion. The strength of environmental stochasticity was then controlled by
$\sigma_e$. Response diversity was controlled by the correlation among species
stochastic mortality rates ($\rho_{ij, i \neq j}$) such as response diversity is
maximal when the stochastic component of species mortality rates ($\epsilon_{i,
t}$) are uncorrelated ($\rho = 0$), and response diversity is null when the
stochastic component of species mortality rates are perfectly correlated ($\rho
= 1$) [@ripa_food_2003; @vasseur_environmental_2007; @gouhier_synchrony_2010].
So the species mortality rates were a product of the stochastic mortality rates
generated by the Ornstein-Uhlenbeck process and a variance-covariance matrix
such as:


\begin{equation}
\begin{aligned}
\epsilon_{i, t} =
  \begin{bmatrix}
     \rho_{11}\sigma^2_e & \rho_{12}\sigma^2_e & \cdots & \rho_{1n}\sigma^2_e \\
     \rho_{21}\sigma^2_e & \rho_{22}\sigma^2_e & \cdots & \rho_{2n}\sigma^2_e \\
     \vdots  & \vdots  & \ddots & \vdots  \\
     \rho_{n1}\sigma^2_e & \rho_{n2}\sigma^2_e & \cdots & \rho_{nn}\sigma^2_e
  \end{bmatrix}
  \begin{bmatrix}
     a_{1,t} \\
     a_{2,t} \\
     \vdots  \\
     a_{n,t}
  \end{bmatrix}
(\#eq:rho)
\end{aligned}
\end{equation}

Where $a_{i,t}$ is the stochastic value generated by the Ornstein-Uhlenbeck process
at time $t$, $\rho_{ii} = 1.0$ while all $\rho_{ij, i \neq j}$ were equal and
control the level of response diversity. All interspecific correlations being
equal, we assume no structure in response diversity across the trophic levels,
which can contrast with the original definition that considered response
diversity as the diversity of species responses within functional groups
[@elmqvist_response_2003].

## Simulation design

```{r}
tar_load(sim_param_tab)
spt <- sim_param_tab
get_sim_par_val <- function(x = "S", data = sim_param_tab) {
  x <- data[data$Parameter == x,][c("min", "max", "n")]
  setNames(unlist(x), c("min", "max", "n"))

}
pS <- get_sim_par_val(x = "S")
pct <- round(get_sim_par_val(x = "ct"), 2)
pZ <- get_sim_par_val(x = "Z")
pc <- get_sim_par_val(x = "c")
pe <- get_sim_par_val(x = "env_stoch")
prd <- get_sim_par_val(x = "resp_div")
pr <- get_sim_par_val(x = "rho")
```

```{r}
tar_load(sim_summary_stat)
m_sim <- function(
  v = "stab_com",
  data = sim_summary_stat,
  col = "Median (5%, 95%)"
  ) {
  data[data$var %in% v, ][[col]]
}
```
```{r, eval = FALSE}
m_sim(v = c("stab_com", "async"))
m_sim(c("stab_com", "async"))
m_sim(col = "n")
```

We generated food web structure using the niche model [@williams_simple_2000]
with an initial species richness from $`r pS["min"]`$ to $`r pS["max"]`$, and
connectance from $`r pct["min"]`$ to $`r pct["max"]`$ (Table S1). We required
food webs without cannibalistic links and fully connected, i.e. we discarded
food webs that contained disconnected species.

We varied the strength of environmental stochasticity by varying $\sigma_e$ from
$`r pe["min"]`$ to $`r pe["max"]`$, the range of mortality rates observed in
protists [@vasseur_environmental_2007]. We decreased response diversity by
increasing $\rho$ from $`r pr["min"]`$ to $`r pr["max"]`$ (i.e. response
diversity is $1 - \rho$) (Fig. S1).

We varied the body mass structure of the food web to vary trophic interaction
strength and mortality rates, because metabolic and mortality rates ($x_i$ &
$d_i$) scale with species body mass. To do so, we varied the predator-prey mass
ratio ($Z$) from $`r pZ["min"]`$ to $`r pZ["max"]`$ (Fig. S1b). Species body
masses ($M_i$) were computed as: $M_i = Z^{TL_i - 1}$, where $TL_i$ is the
trophic level of species $i$. We set $h = 2$, i.e. a functional response of type
III (eq. \@ref(eq:holling)), and varied predator interference (i.e. from $c =
`r pc["min"]`$ to $c = `r pc["max"]`$, eq. \@ref(eq:holling)), as predator
interference was shown to have a tremendous role on population stability
[@brose_allometric_2006]. In the absence of environmental stochasticity and with
a type III functional response, species dynamics reach a steady state without
visible oscillations. We set uniform consumer preferences for their $n$
resources such as: $\omega_{ij} = 1 / n$, half-saturation rate to $B_0=0.5$,
the maximum consumption rate to $y_i = 4$, $r_i=1.0$ based on previous studies
[@brose_allometric_2006].
Intraspecific competition was set to unity ($\alpha_{ii} = 1.0$) and
interspecific competition ($\alpha_{ij, i \neq j}$) to 0.5. We set a global
carrying capacity of $K' = 10$ to ensure that consumers were not limited by the
biomass input from primary producers. We standardised the carrying capacity by
the number of primary producers and by the interspecific competition among
producers to ensure that the effects of species richness on temporal stability
are not driven by the increase in the number of primary producers, thereby
trivially increasing biomass input for consumers. We then standardised $K'$ such
as $K_i = \frac{1 + \alpha_{ij} (S_{prod.} - 1)}{S_{prod.}}K'$
[@ives_stability_2000], where $S_{prod.}$ is the number of primary producer
species. However, we found that our results were not affected when removing the
standardisation of carrying capacity (Fig. S2).

We numerically solved the stochastic differential equation systems during at
least 2000 timesteps and collected the last 500 timesteps, similarly to previous
studies [@brose_allometric_2006]. We numerically solve the system with $\Delta_t
= 0.1$ or $\Delta_t = 0.05$ when instability was detected during the simulations
due to stiff changes in biomass. We set extinction threshold to
$10^{-6}$ and if an extinction happened in the last 500 timesteps, we continued
to run the simulation for another 1000 timesteps until there was no extinction
events during the last 500 timesteps. When we found disconnected species at the
end of the simulation (i.e. a primary producer without consumer or a consumer
without prey), we set their biomass to 0 and re-run the simulation for another
1000 timesteps. Except in the case of disconnected species, we re-ran
simulations with species starting biomass equal to their biomass at the last
timestep of the previous simulation. Supplementary analysis showed that
alternative choices of simulation processes, such as longer simulations,
rebuilding food webs (i.e. resetting consumer preferences, recomputing species
body mass according to the new food web) after removing disconnected species did
not affect our results (Fig. S2). The food web generation and simulations were
done in Julia by developing an extension of the package
`EcologicalNetworksDynamics.jl` [@lajaaiti_ecologicalnetworksdynamicsjl_2024].

In sum, we generated `r format(m_sim(col = "n"), scientific = FALSE)`
simulations over a wide range of food web structure (Median (5%, 95%),
species richness: `r m_sim("richness")`, connectance: `r m_sim("ct_alive")`,
average interaction strength: `r m_sim("avg_int_strength")`, maximum trophic
level: `r m_sim("max_tlvl")`) (Table S2).

## Simulation output generation

We measured food web properties that have been linked with stability in the
literature. We measured total biomass, species richness, connectance, average
trophic level weighted by biomass, average omnivory, and average interaction
strength. Food web properties were measured at each of the 500 timesteps and
then averaged, except connectance and trophic level that were static.
Connectance was computed as $C = L / S(S-1)$, where $L$ is the number of trophic
links and $S$ is the number of species in the community. Species trophic
level was computed recursively from the bottom of the food web, such as the
trophic level of a consumer was equal to the average trophic level of its
resources added to 1, the trophic level of primary producers was set to 1
[@christensen_ecopath_1992]. Average trophic level ($\hat{wTL}$) was then equal to:
$\hat{wTL} = \sum_{i}1/\hat{B_i} \times \mathrm{TL}_i$, where $\mathrm{TL}_i$ is the trophic level and
$\hat{B_i}$ the average biomass of the species $i$. The degree of omnivory of a
consumer was computed such as the sum of squares of its resource trophic levels
weighted by the relative preference of the consumer for each resource: $\sum_i
(\mathrm{TL}_i - \hat{\mathrm{TL}})^2 \omega_i/ \sum \omega_i$
 [@christensen_ecopath_1992]. Interaction strength was computed was quantified as
the biomass fluxes going from every consumer/resource pair, such as: $I_{ij} = x_i y_i
B_i F_{ij}$ (eq. \@ref(eq:cons)), and averaged over time. Our way of measuring
interaction strength is very similar to previous metrics used in previous
studies, at the difference here that we average fluxes over time and not the
maximal interaction strength [@mccann_weak_1998]. Finally, the average
interaction strength of a community was computed as the average of the
$S \times S$ interaction strength matrix at the exclusion of null interaction strengths
(i.e. excluding absence of trophic interactions).

We assessed the effects of food web structure, environmental stochasticity and
response diversity on the temporal stability of community biomass ($S_{com}$).
We measured temporal stability of biomass as the inverse of the coefficient of
variation. We further partitioned stability into population stability
($S_{pop}$) and asynchrony ($\phi$) such as:

\begin{equation}
\begin{aligned}
S_{com} = S_{pop} \times \phi
(\#eq:scom)
\end{aligned}
\end{equation}

with $S_{com} = \mu_{tot} / \sigma_{tot}$, $S_{pop} = \mu_{tot} / \sum_i \sigma_i$,
$\phi = \sum_i \sigma_i / \sigma_{tot}$; where $\mu_{tot}$ and $\sigma_{tot}$
are respectively average total biomass and standard deviation of total biomass.

To further get a mechanistic insight about the effects of environmental
stochasticity, response diversity, and food web structure on stability, we
partitioned asynchrony into portfolio effects ($PFE$) and compensatory dynamics
stemming from species interactions [@zhao_biodiversity_2022] ($CPE_{int}$). The
measurement of portfolio effects has been a topic of debate
[@loreau_biodiversity_2021;@zhao_biodiversity_2022]. Doak's definition
[@doak_statistical_1998] defines portfolio effects as the product of statistical
averaging effects ($SAE$) and compensatory effects arising from response
diversity [@zhao_biodiversity_2022; @doak_statistical_1998] ($CPE_{env}$). It
then quantities the portfolio effect ($PFE = SAE \times CPE_{env}$) emerging
from independent species fluctuations, i.e. the statistical averaging effect
($SAE$), weighted by the effects of response diversity of species to
environmental fluctuations, such as portfolio effects are dampened if species
have correlated responses to environmental fluctuations. To compute portfolio
effects and compensatory dynamics stemming from species interactions, we i)
partition asynchrony into statistical averaging effect and compensatory dynamics
(i.e. $\phi = SAE \times CPE$, eq. \@ref(eq:scom2)); and ii) partition
compensatory dynamics originating from species interactions ($CPE_{int}$) and
from response diversity ($CPE_{env}$).

\begin{equation}
\begin{aligned}
S_{com} &= S_{pop} \times SAE \times CPE \\
S_{com} &= S_{pop} \times SAE \times CPE_{int} \times CPE_{env}
(\#eq:scom2)
\end{aligned}
\end{equation}

Statistical averaging effect ($SAE$) is the share of asynchrony assuming that species are
independent, meaning that the variance total of the community is equal to the
sum of species variances only (i.e. species covariances are null). We can
define community stability ($S_{com, IP}$) in that scenario and then derive $SAE$:

\begin{equation}
\begin{aligned}
S_{com, IP} &= \dfrac{\mu_{tot}}{\sqrt{\sum_i \sigma^2_i}} = SAE \times S_{pop} \\
SAE &= \dfrac{S_{com, IP}}{S_{pop}} = \dfrac{\sum_i \sigma_i}{\sqrt{\sum_i \sigma^2_i}}\\
\end{aligned}
(\#eq:sae2)
\end{equation}

Compensatory dynamics in the food webs is then the remaining part of asynchrony:

\begin{equation}
\begin{aligned}
CPE &= \dfrac{S_{com}}{SAE \times S_{pop}} = \dfrac{\sqrt{\sum_i \sigma^2_i}}{\sigma_{tot}}\\
\end{aligned}
(\#eq:cpe)
\end{equation}

Compensatory effects can arise from predator-prey interactions
($CPE_{int}$) or from differential response of species to environmental
stochasticity ($CPE_{env}$). We computed $CPE_{env}$ on the part of
biomass fluctuations that are due to environmental stochasticity and response
diversity ($\mathbf{B_{d, i}}$, eq. \@ref(eq:cpenv)), i.e. from the
deterministic and stochastic parts of mortality rates. To do so, we used the
time x species matrices of species biomass $\mathbf{B}$ and stochastic mortality
rates $\mathbf{E}$:

\begin{equation}
\begin{aligned}
\mathbf{B_{d, i}} &= \mathbf{B} \times \mathrm{diag}(d_i) \times e^\mathbf{E}
\end{aligned}
(\#eq:cpenv)
\end{equation}

We computed $CPE_{env}$ using the equation \@ref(eq:cpe) with the time x species
matrix ($\mathbf{B_{d, i}}$), so that compensatory effects due to environmental
fluctuations are mainly determined by response diversity (Fig. S3). Then
compensatory effects raising from species interactions were computed as:
$CPE_{int} = CPE / CPE_{env}$. Finally, portfolio effects ($PFE$) were computed
as: $PFE = SAE \times CPE_{env}$ and compensatory effects raising from species
interactions as $CPE_{int}$. The final stability decomposition reads as follows:

\begin{equation}
\begin{aligned}
S_{com} = S_{pop} \times PFE \times CPE_{int}
(\#eq:scom3)
\end{aligned}
\end{equation}

## Statistical analysis

Using a structural equation model, we disentangled the complex effects of food
web structure, environmental stochasticity and response diversity on the
different facets of temporal stability of biomass (i.e. population stability,
asynchrony, portfolio effects and compensatory dynamic effects). We tested the
effects of food web structure (average interaction strength, average trophic
level, connectance) on population stability and asynchrony partitions (portfolio
and compensatory effects). The structure of the structural equation model was
defined a priori based on expectations from previous theoretical studies. Then, we
expected that higher average trophic level, lower interaction strength, lower
connectance result in higher population stability and lower asynchrony
[@mccann_weak_1998; @mccann_reevaluating_1997; @mccann_diversitystability_2000;
@fahimipour_compensation_2017]. We further added simulation parameters as
control variables because higher Predator-Prey Mass Ratio and predator
interference were also expected to increase population stability
[@brose_allometric_2006]. Average omnivory was not included because the
collinearity (i.e. measured by the Variance Inflation Factor) with average
trophic level was too high. Finally, we tested the effects of environmental
stochasticity and response diversity on population stability and asynchrony
partitions, although there were predicted to mainly affect population stability
(i.e. by increasing amplitude of population fluctuations) and asynchrony (i.e.
by generating independent population fluctuations) respectively. We completed
the structural equation model with the mathematical relationship linking
compensatory dynamics due to species interactions ($CPE_{int}$) and statistical
averaging effects ($SAE \times CPE_{env}$) to asynchrony, and from asynchrony
and population stability to community stability.

Prior testing the structural equation model, we logged all the stability
components to transform their relation from multiplicative to additive (eq.
\@ref(eq:scom2)). We ensured that all the linear models composing the structural
equation model presented low multicollinearity (Variance Inflation Factor < 3,
Table S3), although interaction strength and species richness were highly
correlated (Fig. S4). The structural equation model was evaluated using the R package
`PiecewiseSEM` [@lefcheck_piecewisesem_2016]. We computed the sum
of the direct and indirect effects using `semEff` R
package [@murphy_semeff_2021]. In the main text, we reported standardised
coefficients which were obtained by scaling the coefficients by the standard
deviation of the response and predictor variable. Finally, we reported only the
direct standardised coefficients with an absolute value equal or above $0.05$,
because almost all effects were statistically significant given the high numbers
of simulations. These direct standardised coefficients reflect partial
correlation coefficients, while total standardised coefficients reflect
correlation coefficients [@grace_structural_2006].

In a second analysis, we tested how food web structure, response diversity, and
environmental stochasticity modulate stability-species richness relationships.
We modelled temporal stability of community biomass according to food web
structure: species richness, weighted average trophic level, connectance and
average interaction strength, as well as environmental stochasticity and
response diversity. We further included the two-way interactions between species
richness and food web structure, between species richness and response
diversity, between species richness and environmental stochasticity. Finally, we
added the three-way interactions between species richness, food web structure
and response diversity, between species richness, food web structure and
environmental stochasticity. We added predator interference, predator-prey mass
ratio as control variables. We further added the ID of the food web as a random
intercept. We then used the linear equation of the model and associated slope
coefficients to predict the shape of the relationship between community
stability and species richness according to a gradient of response diversity and
of food web structure. To do so, we summed all the coefficients involving
species richness in the model, i.e. the one, two, and three-way terms. The
values of the other variables were set to the values indicated in the Fig.
\@ref(fig:pred). The coefficients of the models are displayed in Fig. S5. The
VIFs were inferior to 3, indicating low multicollinearity (Table S4), we checked
the distribution of the residuals (Fig. S6) using `DHARMa` R package. The model
was implemented using the R package `glmmTMB` [@brooks_glmmtmb_2017].

# Results

```{r}

sem_cap <- paste0(
  "Structural Equation Model linking food web structure and stressors to the
  temporal stability of community biomass. a, Continuous blue arrows display
  positive and dashed red arrows display negative standardised effects, the
  arrow widths are proportional to the absolute values of the standardised
  effects. Only the standardised coefficients whose absolute values are superior
  to 0.05 are displayed. The full table of coefficients including control
  variables is displayed in Table S5. b, Total effects of food web structure on
  community stability, asynchrony, and population stability derived from the
  structural equation model. N = ", nrow(tar_read(sim_fw)), " simulations.") %>%
  str_replace_all("\\s+", " ")
```

```{r sem, fig.cap=sem_cap, fig.id = "sem"}
knitr::include_graphics(here::here("report", "figures", "p_sem_fig.pdf"))
```

```{r}
tar_load(c(sem_doak_eff_tab, sem_simplified_eff_tab))

```

```{r fig2-coeff, eval = FALSE}
tar_read(sem_fig_coeff)
tar_read(sem_doak_rsquared_csc_rerun)
```



```{r}
get_eff <- function(
  y = "pop_stab", x = "richness",
  d = 2, effect_type = "direct",
  tab = sem_doak_eff_tab) {
  mask <- tab$response == y & tab$predictor == x &
    tab$effect_type == effect_type
  round(tab[mask, ]$effect, d)
}

rpt <- get_eff(y = "pop_stab", x = "w_avg_tlvl")
rpc <- get_eff(y = "pop_stab", x = "c")
rpe <- get_eff(y = "pop_stab", x = "env_stoch")
rpd <- get_eff(y = "pop_stab", x = "resp_div")

rsr <- get_eff(y = "sae_doak", x = "richness")
rst <- get_eff(y = "sae_doak", x = "w_avg_tlvl")
rsi <- get_eff(y = "sae_doak", x = "avg_int_strength")
rsc <- get_eff(y = "sae_doak", x = "ct_alive")

rcr <- get_eff(y = "cpe_int", x = "richness")
rci <- get_eff(y = "cpe_int", x = "avg_int_strength")
rct <- get_eff(y = "cpe_int", x = "w_avg_tlvl")
rcd <- get_eff(y = "cpe_int", x = "resp_div")
rcc <- get_eff(y = "cpe_int", x = "ct_alive")

# Detailled SEM coefficients
rsr <- get_eff(y = "sae_doak", x = "richness")
rst <- get_eff(y = "sae_doak", x = "w_avg_tlvl")
rsr <- get_eff(y = "sae_doak", x = "richness")
rsa <- get_eff(y = "sae_doak", x = "avg_int_strength")
rsct <- get_eff(y = "sae_doak", x = "ct_alive")
rsc <- get_eff(y = "sae_doak", x = "c")
rsd <- get_eff(y = "sae_doak", x = "resp_div")

```


```{r}
rscp <- get_eff(y = "stab_com", x = "pop_stab")
rsca <- get_eff(y = "stab_com", x = "async")

rac <- get_eff(y = "async", x = "cpe_int")
ras <- get_eff(y = "async", x = "sae_doak")
tar_load(sim_fw_sem)
```

## The drivers of community stability

Applying a structural equation model on the outcomes of food web simulations
revealed that the temporal stability of community biomass is
positively influenced by both population stability and asynchrony, and that
population stability has twice the effect of asynchrony (resp. $r_\delta$=
`r rscp` and `r rsca`, $r_\delta$ is the standardised coefficient, Fig.
\@ref(fig:sem)a). This result might be driven by the relative variance of
environmental stochasticity and response diversity explored in our simulations,
such as higher variance in environmental stochasticity relative to response
diversity would result in higher variance in population stability than in
asynchrony. However the standard deviation of environmental stochasticity was twice
lower than response diversity (resp. `r round(sd(sim_fw_sem$env_stoch), 2)` vs
`r round(sd(sim_fw_sem$resp_div),2)`). All the tested causal relationships are
presented in Table S5.

We further found that asynchrony is driven more by portfolio effects than by
compensatory dynamics (resp. $r_\delta$= `r ras` and `r rac`). In more details, response
diversity has strong positive effects on asynchrony, mainly through portfolio
effects ($r_\delta$= `r rsd`), at the expense of compensatory
dynamics ($r_\delta$= `r rcd`). All other studied properties were found to have relatively
much weaker effects on asynchrony. Food web structural properties – namely
average trophic level, connectance and average interaction strength – have
consistent negative effects on asynchrony, through both portfolio and
compensatory effects (Fig. \@ref(fig:sem)a). Indeed, as average trophic level and connectance
increase compensatory effects are reduced (resp. $r_\delta$= `r rct` and `r rcc`, Fig.
\@ref(fig:sem)a), while average interaction strength has a small negative effect
on portfolio effects ($r_\delta$= `r rsi`). Species richness has a positive
effect on both portfolio and compensatory effects (resp. $r_\delta$= `r rsr` and
`r rcr`). Finally, as expected, environmental stochasticity has little effect on
asynchrony.

Focusing on population stability, environmental stochasticity was found to have
a strong negative effect on it ($r_\delta$= `r rpe`). All other studied properties were
found to have little effect on population stability, except for the average
trophic level which has a small positive effect ($r_\delta$= `r rpt`, Fig.
\@ref(fig:sem)a, but see Fig. S2) and response diversity a small negative effect
($r_\delta$= `r rpd`).

```{r}
rtsdiv <- get_eff(y = "stab_com", x = "resp_div", effect_type = "total")
rtsenv <- get_eff(y = "stab_com", x = "env_stoch", effect_type = "total")

rtsr <- get_eff(y = "stab_com", x = "richness", effect_type = "total")
rtst <- get_eff(y = "stab_com", x = "w_avg_tlvl", effect_type = "total")
rtsz <- get_eff(y = "stab_com", x = "Z", effect_type = "total")
rtsc <- get_eff(y = "stab_com", x = "c", effect_type = "total")
rtsct <- get_eff(y = "stab_com", x = "ct_alive", effect_type = "total")
rtsi <- get_eff(y = "stab_com", x = "avg_int_strength", effect_type = "total")

rtpr <- get_eff(y = "pop_stab", x = "richness", effect_type = "total")
rtpt <- get_eff(y = "pop_stab", x = "w_avg_tlvl", effect_type = "total")
rtpi <- get_eff(y = "pop_stab", x = "avg_int_strength", effect_type = "total")
rtpz <- get_eff(y = "pop_stab", x = "Z", effect_type = "total")
rtpc <- get_eff(y = "pop_stab", x = "c", effect_type = "total")
rtpct <- get_eff(y = "pop_stab", x = "ct_alive", effect_type = "total")

rtar <- get_eff(y = "async", x = "richness", effect_type = "total")
rtat <- get_eff(y = "async", x = "w_avg_tlvl", effect_type = "total")
rtai <- get_eff(y = "async", x = "avg_int_strength", effect_type = "total")
rtaz <- get_eff(y = "async", x = "Z", effect_type = "total")
rtac <- get_eff(y = "async", x = "c", effect_type = "total")
rtact <- get_eff(y = "async", x = "ct_alive", effect_type = "total")
```

Deriving total effects from the sum of direct and indirect effects in the
structural equation model (See Method), we showed that both environmental
stochasticity and species response diversity have by far the strongest total
effects on community stability (resp. $r_\delta$= `r rtsenv` and `r rtsdiv`,
Fig. \@ref(fig:sem)b). Species richness and average trophic level have similar
small but positive total effects on community stability ($r_\delta$= `r rtsr`),
but through opposite pathways. While species richness increases community
stability through a strong positive effect on asynchrony ($r_\delta$= `r rtar`),
it also weakly decreases population stability ($r_\delta$= `r rtpr`). In
contrast, average trophic level increases community stability through strong
positive effect on population stability ($r_\delta$= `r rtpt`), but is dampened
by a negative total effect on asynchrony ($r_\delta$= `r rtat`). Interestingly,
average interaction strength also has a positive effect on population stability
and a negative one on asynchrony (resp. $r_\delta$= `r rtpi` and `r rtai`). This
results in a total negative effect on community stability ($r_\delta$=
`r rtsi`). Connectance, instead, has a negative effect on community stability
($r_\delta$= `r rtsct`) through negative effects on both asynchrony and
population stability (resp. $r_\delta$= `r rtact` and `r rtpct`).

```{r}
tar_load(default_variable_values_pred)
pv <- default_variable_values_pred

pv_cap <- paste0(
  "connectance = ", round(pv["ct_alive"], 2),
  ", average interaction strength = ", round(pv["avg_int_strength"], 3),
  ", average trophic level = ", round(pv["w_avg_tlvl"], 2),
  ", predator interference = ", round(pv["c"], 1),
  ", Predator-Prey Mass Ratio = ", round(pv["Z"]),
  ", and environmental stochasticity = ", round(pv["env_stoch"], 1)

)
pred_cap <- paste0("Slope of the community stability - species
  richness relationship based on food web structure and response diversity. a,
  Diagrams displaying the slope coefficients of the effect of species richness
  on community stability. The average values of the control variables were used
  to generate the predictions: ", pv_cap, ". b, c: Examples of predictions
  from the model for two combinations of average trophic level and response
  diversity (values displayed in panel a). Lines display the mean predictions of
  the model. The coefficients of the linear model are displayed in Fig. S4.
  Relationships between population stability, asynchrony and species richness
  are displayed in Fig. S7.
  "
  ) %>%
  str_replace_all("\\s+", " ")
```



```{r pred, fig.cap = pred_cap, fig.id = "pred"}
knitr::include_graphics(here("report", "figures", "p_fig3.pdf"))
```

## The context dependence of stability - richness relationships

We further assessed how environmental stochasticity and response diversity
interacted with food web structural properties to determine the sign of the
stability-richness relationship, using a linear model including main effects and
all interactions among food web structural properties, response diversity and
environmental stochasticity (see Methods). We found that there are strong
interactions between response diversity and food web structure, which jointly
determine the sign of the stability-richness relationship.

In the absence of response diversity, we found only negative stability-richness
relationships, regardless of the food web structure (Fig. \@ref(fig:pred)a).
Response diversity enables the rise of positive stability-richness
relationships, enhanced by average interaction strength and dampened by average
trophic level and connectance. Higher interaction strength leads to positive
stability-richness relationships for lower values of response diversity, and
interaction strength enhances asynchrony-richness relationships (Fig. S7), so
that the stronger positive stability-richness relationships are found at both
high interaction strength and high response diversity levels. In contrast,
higher average trophic level and connectance both lead to negative
stability-richness relationships, because they drive more negative population
stability-richness relationships and weaker positive asynchrony-richness
relationships (Fig. S7). Overall, our results highlight a strong contrast
between the relatively small effects of food web structural properties on
overall community stability (Fig. \@ref(fig:sem)b) but their strong effects on
the slope of the stability-richness relationship (Fig. \@ref(fig:pred)a).


```{r, eval = FALSE}
tar_read(p_int_fw_str)
```

# Discussion

With the projected changes in climate and land use, and the associated  changes
in community composition (e.g. loss of diversity, change in structure,
homogenisation), it is important to understand the mechanisms which allow
ecological communities to remain stable despite perturbations. Recent research
has focused on  the average stability of the populations composing the community
and the asynchrony of the population fluctuations on the other hand [@thibaut_understanding_2013;
@zhao_biodiversity_2022]. Much of this previous work has been done in
simplified assemblages, such as single trophic level communities, and in this
context here community stability has been shown to be driven by asynchrony in
species fluctuations, rather than by population stability [@olivier_urbanization_2020].
However, whether this holds for more complex trophically structured ecological
communities, such as food webs, remains largely unknown. Here, we tackled this
question using simulations of complex, stochastic food web dynamics via a
bioenergetic model. This integration of complex food webs to the other factors
driving stability is needed to contextualise and predict diversity - stability
relationships amidst rapid global environmental change.

Our model results show that, in complex food webs, community stability is more
driven by population stability than by asynchrony, in contrast with what was
observed in single trophic level communities. Our study further reveals that the
main drivers of community stability are environmental stochasticity and response
diversity, respectively acting on population stability and asynchrony.
One trivial explanation for this pattern might be the ratio of variance from
environmental stochasticity to response diversity explored in our simulations,
as a higher variance in environmental stochasticity relative to response
diversity would result in higher effect size in population stability than in
asynchrony because those coefficients were expressed relative to the standard
deviation of the variables (i.e. standardised coefficients). However the
standard deviation of environmental stochasticity was 2x  lower than response
diversity (resp. 0.17 vs 0.35), so  that the higher importance of population
stability relative to asynchrony that we report cannot be explained by the
explored parameter ranges in the study.

An additional key finding is that despite previous work in simple communities
suggesting that food web structural properties drive stability, we found that
these properties have much weaker effects in more complex food webs, a result
consistent across a diversity of simulation methodologies (Fig. S2). However,
structural properties are central to our understanding of stability-richness
relationships. They were found to play an important role in the sign of the
stability-richness relationship, which is strongly mediated by the interaction
between food web structure and response diversity. These results highlight the
dual importance of response diversity to improve our understanding of the
stability of structured ecological communities in variable environments.  In the
following sections, we deliver more nuanced insight into these conclusions.


## Environmental Stochasticity and response diversity are the main drivers of community stability

We found environmental stochasticity and response diversity to be the main
overall drivers of community stability. While environmental stochasticity
decreases population stability, response diversity generates asynchrony, thereby
buffering environmental stochasticity. This result is in accordance with
previous theoretical and empirical findings in competitive communities
[@thibaut_diversity_2012; @thibaut_understanding_2013; @thebault_trophic_2005;
@loreau_species_2008; @de_mazancourt_predicting_2013; @ives_stability_2000]. In
turn, response diversity was found to operate on asynchrony. This is in
agreement with empirical findings in competitive assemblages where response
diversity was quantified with trait-based or non trait-based approaches
[@thibaut_diversity_2012; @sasaki_species_2019; @zhao_biodiversity_2022].
Specifically in our model, response diversity was driving portfolio effects
through compensatory effects due to species' differential responses to
environmental fluctuations (i.e.
$CPE_{env}$, see methods eq. \@ref(eq:cpe)-\@ref(eq:scom3)), thereby modulating
the statistical averaging of independent species fluctuations
[@doak_statistical_1998]. This mechanism highlights how differences in species'
environmental responses contribute to asynchrony, stabilizing communities by
reducing the synchrony of population fluctuations.

A consequence of the large effect of response diversity is that asynchrony in
species fluctuations is driven more by the statistical averaging of independent
species fluctuations weighted by response diversity (portfolio effects) than by
compensatory dynamics emerging from species interactions. This finding is also
coherent with previous studies in competitive communities
[@thibaut_diversity_2012; @zhao_biodiversity_2022], but it was less expected to
happen in food webs. Trophic interactions are indeed expected to result in more
compensatory dynamics resulting from oscillations between predators and prey
[@vandermeer_coupled_2004] or prey switching from predators [@mccann_weak_1998;
@mccann_diversitystability_2000]. However, pioneering theoretical studies have
shown that environmental stochasticity can dampen prey switching
[@vasseur_environmental_2007] and that trophic cascades between trophic levels
in species rich food webs are weak compared to food chains and species poor food
web modules [@fahimipour_compensation_2017]. So, the question of the importance
of compensatory dynamics in complex food webs remains an open and interesting
avenue for future research.

In contrast to empirical evidence in competitive communities
[@olivier_urbanization_2020], population stability (not asynchrony) was found to
be the dominant driver of community stability in our food web simulations. These
results are in agreement with previous findings in empirical food webs
[@danet_species_2021] and food web models [@eschenbrenner_diversity_2023], which
suggest fundamental differences between competitive communities and food webs in
the relative contributions of population stability and asynchrony to community
stability. Our findings suggest that the presence of trophic links contributes
to synchronise the species of the community because we found that the food web
metrics studied – namely average trophic level, connectance, and average
interaction strength – all decrease asynchrony. These results are in line with
empirical evidence that predators can synchronise their prey
[@raimondo_interspecific_2004; @korpimaki_predatorinduced_2005], and that
species pairs involved in trophic interactions are more synchronous than those
that are not [@danet_species_2021]. A complementary explanation for the
relatively lower importance of asynchrony in food webs (compared to single
trophic level communities) could be related to the biomass structure of food
webs. food webs typically include a larger range of body masses than single
trophic level assemblages [@brose_predator_2019]. Such highly uneven biomass
distribution can translate in uneven species temporal variability, thereby
creating uneven species contributions to asynchrony
[@thibaut_understanding_2013] and limiting portfolio effects and compensatory
dynamics in species-rich communities [@zhao_biodiversity_2022].

Investigating in more detail the drivers of community stability, our results
suggest that species richness and the network structural properties investigated
only have a weak effect on overall community stability. We found that higher
average trophic level leads to higher community stability by increasing average
population stability, confirming previous theoretical
[@shanafelt_stability_2018; @eschenbrenner_diversity_2023;
@brose_allometric_2006] and empirical [@danet_species_2021] results. However,
this effect disappeared when we simulated community dynamics with equal
mortality rates for all species instead of allometric ones (Fig. S2). This
suggests that the higher stability of food webs with higher average trophic
levels stems more from their lower mortality rates rather than from their
trophic role directly. The overall effect of connectance on overall community
stability was found to be quite low, in agreement with previous empirical and
theoretical findings [@danet_species_2021; @eschenbrenner_diversity_2023].
Similarly, we found very low effects of the average interaction strength on
community stability, which is in apparent disagreement with the predominant role
of interaction strength and connectance on stability [@may_will_1972]. We found
that average interaction strength had a weak positive effect on population
stability, in confirmation with previous theoretical findings aligning with our
model assumption that there was no asymmetry of consumer preferences for their
prey [@gellner_consistent_2016].

## Stability-richness relationships depend on response diversity and food web structure

Our results also allow us to revisit the old question of the relationship
between the complexity of ecological communities and their stability
[@may_will_1972; @angelis_stability_1975]. We found that response diversity
enables the rise of positive stability-richness relationships, enhanced by
average interaction strength and dampened by average trophic level and
connectance. In the absence of response diversity, only negative relationships
between community stability and species richness are observed. This reinforces
the idea that increases in species richness increase community stability only if
the added species have different responses to environmental perturbations, i.e. if
there is response diversity [@de_mazancourt_predicting_2013;
@thebault_trophic_2005]. Indeed, a community with numerous species which respond
differently to environmental change is more likely to buffer a wide array of
perturbations [@yachi_biodiversity_1999; @ives_stability_2000]. Despite its
relatively weaker effect on community stability (than response diversity and
environmental stochasticity), food web structure interacts strongly with
response diversity to determine the sign of stability-richness relationships.
Surprisingly, we find that higher average interaction strength enhances positive
stability-richness relationships by enhancing asynchrony-richness relationships.
Conversely, higher average trophic level and higher connectance both led to
negative stability-richness relationships by dampening asynchrony-richness
relationships. It would appear that asynchrony becomes too weak to compensate
for the simultaneous decrease in population stability induced by increasing
species richness.

These results should be understood as the predicted stability-richness
relationships if food web structure is kept constant, i.e. if food web structure
does not vary with species richness. However, connectance [@dunne_network_2006]
and average trophic level weighted by biomass are documented to decrease with
species richness [@danet_species_2021], because of energetic and topological
constraints [@dunne_network_2006; @gravel_trophic_2011]. Our results add to this
body of work by suggesting that ecological communities that do not decrease in
connectance and average trophic level while increasing in species richness,
should decrease in stability. Our results resonate with findings that some
community structure can lead to negative stability-richness relationships, as
previously reported in freshwater food webs [@danet_species_2021]. Response
diversity might therefore be one of the mechanisms that explains why positive
relationships between stability and species richness are so prevalent in
empirical settings [@elmqvist_response_2003; @thibaut_understanding_2013], while
food web theoretical models that do not often include environmental
stochasticity and response diversity typically find negative
complexity-stability relationships [@ives_stability_2007].

## Summary

In conclusion, our study highlights the contrasting effects of response
diversity and food web structure on the temporal stability of species rich
communities: response diversity underpins community stability and strongly
interacts with food web structure to define stability-richness relationships. In
line with the insurance hypothesis [@yachi_biodiversity_1999;
@loreau_biodiversity_2021], our results suggest that environmental stochasticity
and response diversity are the main mechanisms driving community stability,
while food web structural properties are only mediating them. This further
aligns with the idea that, in species-rich communities, community structure
might be secondary in understanding the generic effects of biodiversity on
ecosystem functioning [@barbier_generic_2018; @ives_stability_2000]. Our results
further add to mounting evidence that population stability is a stronger driver
of community stability than asynchrony in food webs, in contrast with what was
observed in competitive communities.

The fact that environmental stochasticity was found to be the main driver of
overall community stability raises concerns about the consequences of the
current rise in the frequency and severity of environmental extreme events for
ecological communities [@ghosh_temperature_2024; @lee_ipcc_2023]; indeed our
results suggest that these changes are unlikely to be compensated by biotic
mechanisms alone. Documenting how rapid biodiversity changes
[@dornelas_assemblage_2014; @blowes_geography_2019] driven by human pressures
[@danet_past_2024] – and in particular the reported homogenisation
[@olden_homogocene_2018; @wang_biotic_2021] in community composition – affect
response diversity will be key to accurately predict how it will affect, in
turn, the stability of communities.

Looking forward, we emphasise promising perspectives in further understanding
the temporal stability of ecological communities. Our study brings evidence that
asynchrony is predominantly driven by portfolio effects as previously reported
in plant communities; However, we expect that some ecological contexts could
result in the dominance of compensatory effects due to species interactions over
portfolio effects. An example is the role of the structure of response
diversity, since we here considered species responses correlation across whole
food web communities. We expect that considering species differential responses
to environmental stochasticity within functional groups
[@elmqvist_response_2003], such as trophic levels, may give more importance to
compensatory dynamics due to environmental fluctuations relative to the ones due
to species interactions. The structure of response diversity in food webs has
been overlooked so far, but this knowledge is expected to rise with the
methodological progress in measuring response diversity [@ross_how_2023;
@polazzo_measuring_2024]. Another context to explore is the effect of the
distribution of interaction strength in food webs. Implementing asymmetric
distributions of consumer preferences for their prey could also increase the
importance of compensatory dynamics due to species interactions as strong
asymmetry in interaction strength can enhance prey switching behaviour
[@mccann_weak_1998; @mccann_diversitystability_2000].

## Data accessibility statement

The code used to run the simulations, analyse them and to write the manuscript
is archived anonymously on Zenodo: https://zenodo.org/records/14333268.

# References {-}
