---
title: Food-web structure, stochasticity and response diversity drive temporal stability in complex communities
author: Alain Danet, Andrew P. Beckerman
output:
  bookdown::pdf_document2
always_allow_html: true
toc: false
bibliography: references.bib
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{setspace}\doublespacing
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.pos = "H",  # pdf mode
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE,
  fig.path="figures/"
)
```

```{r, results = FALSE}

sapply(c("targets", "tidyverse", "magrittr", "cowplot", "here", "piecewiseSEM", "semEff", "ggcorrplot", "kableExtra"), require, character.only = TRUE)

mytheme <- theme_cowplot(font_size = 8) +
background_grid() +
theme(legend.position = "bottom")
theme_set(mytheme)
sapply(list.files(here("R"), full.names = TRUE), source)
```

# IDEA, meeting with Sonia

- Simplifying SEM in main text, move details to appendix
- State diagram for stability - richness relationships along two food-web
  metrics and panels varying response diversity.
- Look at the french data for portefolio and compensatory dynamics effects.
- Mid-October

# Abstract

Current biotic homogenization and increasing frequency of extreme events are
projected to dramatically destabilize ecological communities. Understanding how
complex communities such as food-webs respond to such threats is crucial to take
adequate conservation measures. We then investigated how response diversity,
environmental stochasticity, and food-web structure drive temporal stability of
biomass in complex food-webs, using a stochastic bioenergetic food-web model. We
found that higher average trophic level, omnivory degree and generalism
increased  average population stability while species richness had little
effects. At the opposite higher average trophic level, omnivory degree and
generalism decreased asynchrony and compensatory dynamics raising trophic
interactions. We further found that that high interaction strength drive
negative stability-species richness when response diversity is low but that high
response diversity always drive positive stability-richness relationship. Our
study reveals that response diversity and food-web structure drive temporal
stability and further improve our understanding of biodiversity-stability
relationships in complex trophic communities.


# Introduction

Global change and its simultaneous increasing stressors constitute a major
threat to biodiversity and ecosystem functioning [@pachauri_climate_2015;
@simmons_refocusing_2021]. Among them, climate change is predicted to lead
dramatically more variable environments [@pachauri_climate_2015]. Understanding
how environmental variability will affect ecosystem
stability is then a timely question.

Biodiversity, in terms of species richness, has been repeatedly shown to drive
higher temporal stability of ecological communities, across various taxa and
ecosystems. Species richness can dampen the effects of perturbations on the
temporal variability of community biomass because more diverse communities
contain species with more diversity of responses to perturbations, which
generates asynchrony in population fluctuations, thereby stabilizing community
biomass fluctuations [@loreau_species_2008; @thibaut_understanding_2013;
@zhao_biodiversity_2022]. In turn, the effects of human pressures on biotic
homogenization reported in various ecosystems [@buisson_toward_2013;
@muthukrishnan_invasive_2020; @saladin_rapid_2020] is another threat, which
might in turn affect dampens the effects of species richness on ecosystem
stability. However, the joint effects of external stressors such as
environmental variability and internal stressors such as the
loss response diversity has been rarely assessed in temporal stability areas.

The question of stressors can even become complex in multitrophic communities,
where species richness corresponds both to horizontal and vertical diversity.
Food-web structure has been shown to have tremendous effect on community
stability. The degree of generalism of predator was shown to modulate
stability-richness relationships [@thebault_trophic_2005]. The strength and
distribution of interaction strength was also shown to be strong driver of
community stability [@mccann_weak_1998]. Omnivory was also shown to drive higher
stability [@mccann_reevaluating_1997]. The effects of food-web structure on
ecosystem stability has been mostly assessed with small modules [but see
@eschenbrenner_diversity_nodate], and we know very little how food-web structure
affects the relationships between species richness and temporal stability in
complex food-webs.

Both stressors and food-web structure are expected to have different effects on
temporal stability. Stability of community biomass can itself be partitioned in
several components, i.e. population stability and population asynchrony
[@thibaut_understanding_2013; @zhao_biodiversity_2022]. Population stability can
be itself partioned in total biomass and population variability effect.
Population asynchrony can further be partioned in statistical averaging effect
and compensatory dynamics effects [@zhao_biodiversity_2022]. Partitioning
stability allows to better understand how food-web structure and external
factors affect stability. We expect that environmental variability will
primarily affect. For exemple, environmental stochasticity is expected to
primarily affect population variance. Response diversity is expected to act
primarily on compensatory dynamics in the food-webs, as low response diversity
will decrease the effects. Higher connectance and interaction strength are
expected to dampens population variability but to lead to higher synchrony at
the same time.

---
#Understanding the mechanisms that determine temporal
#stability of ecosystem functioning is a long standing
#question in Ecology [@may_will_1972; @angelis_stability_1975;
#@mccann_diversitystability_2000; @tilman_biodiversity_2006;
#@donohue_navigating_2016; @kefi_advancing_2019].
---

In this study, we investigated both the effects of stressors ( environnmental
variability and response diversity) and of food-web structure (connectance,
average interaction strength, average trophic level) on species
richness-stability relationships. To do, we used a bioenergetic food-web model
[@yodzis_body_1992; @brose_allometric_2006; @delmas_simulations_2017] added to
environmental stochasticity.


```{r}
concept_cap <- "Food-web structure, response diversity and enviromental gradient
can modulate stability-richness relationships. (a & b) Food-web structure may
modulate stability-richness relationships additively (a) or interactively (b).
(c) Decrease in response diversity and increase in environmental variability
should dampen stability-richness relationships. While the loss of response
diversity should dampen the effect of species richness on asynchrony, the
increase in environmental variability should decrease primarily population
stability. (d) Increase in productivity should increase species richness
(trophic energy hypothesis) but also dampens the relationship between stability
and species richness (paradox of enrichment). (e) Summary of the framework, how
food-web structure and external perturbations modulate the effects of species
richness on community stability. More precisely, how they affect the different
components of stability: total biomass, population variability, statistical
averaging effects and compensatory dynamics."
```


```{r, eval = FALSE, fig.cap=concept_cap}
knitr::include_graphics(here("report", "figures", "conceptual_figures.pdf"))
```

```{r, eval = FALSE}
tribble(
  ~Type, ~`Food-web structure`, ~`Effect on stability-richness`,
  "Food-web structure", "Connectance", "Strengthen (Miele et al., 2016) / No effect (Thébault & Loreau, 2005)",
  "Food-web structure", "Omnivory", "Strengthen (Mccann et al., 1997)",
  "Food-web structure", "Interaction strength", "Destabilising (Mccann et al., 1998) / Stabilising in
  productive (Binzer et al., 2012; Binzer et al., 2016; Tabi et al., 2019)",
  "Response diversity", "", "Dampens",
  "Productivity", "", "Dampens (Binzer et al., 2012; Binzer et al., 2016; Tabi et al., 2019)",
  "Environmental variability", "", "Dampens",) %>%
kbl(caption = "Predictions of stability-richness relationship from the literature.") %>%
kable_styling()
```

\pagebreak


# Methods

## The model

We simulated the dynamics of complex food-webs using the allometric bioenergetic
model [@yodzis_body_1992; @brose_allometric_2006; @delmas_simulations_2017].
[DESCRIPTION of the  MODEL]

We added a stochastic natural mortality rate to the species dynamics, that
represent variation in mortality due to variation in environment. Based on the
litterature and previous models [@vasseur_environmental_2007], we assumed that
natural mortality rates scales inversely with the species body mass ($d_i =
d_0M_i^{-1/4}$, ), as all other physiological parameters. We used a basal
natural mortality rate of $d_0 = .4$, as done in previous
studies[@vasseur_environmental_2007].

## Environmental stochasticity and response diversity

We introduced environmental stochasticity by
considering stochastic variation of mortality rates. Doing so allows to consider
stochasticity without modifying species interactions themselves
[@vasseur_environmental_2007]. The stochastic part of the mortality rates
($\epsilon_{i, t}$) follow a normal distribution 0 centered
($\epsilon_{i, t} \sim N(0,\sigma^2_e)$) with a variance ($\sigma^2_e$). The mortality rate each
species at the time $t$ equals to $d_{i,t} = d_i e^{\epsilon_{i, t}}$. We did so
to ensure to not have negative mortality rates [@vasseur_environmental_2007]. We
simulated $\epsilon$ using an Ornstein-Uhlenbeck process, which is a modified
browian motion where the stochastic values tend to come back to the central
value (i.e. $\epsilon = 0$) such as $\epsilon_t$ varies according to this
stochastic differential equation: $d\epsilon_t = (0 - \epsilon_t)d_t + \sigma_e
dW_t$, where $dW_t$ is a Browian motion. The strength of environmental
stochasticity was then controlled by $\sigma_e$.

Response diversity was controlled by the correlation  among species stochastic
mortality rates ($\rho_{ij, i \neq j}$) such as response diversity is maximal when species mortality
rates are uncorrelated ($\rho = 0$) and null when species mortality
rates are perfectly correlated ($\rho = 1$) [@ripa_food_2003;
@vasseur_environmental_2007; @gouhier_synchrony_2010]. So the species mortality
rates were a product of the stochastic mortality rates generated by the
Ornstein-Uhlenbeck process and a variance-covariance matrix such as:

$$
\epsilon_{i, t} =
  \begin{bmatrix}
     \rho_{11}\sigma^2_e & \rho_{12}\sigma^2_e & \cdots & \rho_{1n}\sigma^2_e \\
     \rho_{21}\sigma^2_e & \rho_{22}\sigma^2_e & \cdots & \rho_{2n}\sigma^2_e \\
     \vdots  & \vdots  & \ddots & \vdots  \\
     \rho_{n1}\sigma^2_e & \rho_{n2}\sigma^2_e & \cdots & \rho_{nn}\sigma^2_e
  \end{bmatrix}
  \begin{bmatrix}
     a_{1,t} \\
     a_{2,t} \\
     \vdots  \\
     a_{n,t}
  \end{bmatrix}
$$

where $a_{i,t}$ the stochastic value generated by the Ornstein-Uhlenbeck
process at time $t$, $\rho_{ii} = 1.0$ while all $\rho_{ij, i \neq j}$ were equal and control
the level of response diversity.

## Simulation

We generated food-web structure using the niche model [@williams_simple_2000]
with species richness from 10 to 60, and connectance from $0.02$ to $.32$. We
generated food-webs without cannibalistic links and checked for the absence of
disconnected species.

To vary interaction strength and mortality rates in the community,
we varied the Predator-Prey Bodysize Ratio (PPBR) from 1 to 100. We further
varied the functional reponse of consumer from type II to type III (resp. $h=2$
and $h=3$, eq XX) as it was shown to have a tremendous role on stability
[@brose_allometric_2006]. We set $K = XX$ to ensure that consumers were not
limited by the biomass input in the food-web.

We varied the strength of environmental stochasticity by varying $\sigma_e$ from
0.1 to 0.6, the range of mortality rates observed in
protists [@vasseur_environmental_2007]. We decreased response diversity by
increasing $\rho$ from 0 to 1.

We numerically solved the simulation with a $dt$ = .1 during 5000 timesteps
and collected the last 500 timesteps. We set extinction threshold to $10^{-5}$
and if an extinction happened in the last 500 timesteps, we continued to run the
simulation for another 500 timesteps until there was no extinction events.

## Simulation analysis

We measured food-web structure and dynamics that have been shown to be linked
with stability. We collected total biomass, species richness, connectance,
average trophic level weighted by biomass, average omnivory and average per
capita interaction strength.

We assessed the effects of food-web structure, environmental stochasticity and
response diversity on temporal stability of biomass. We measured temporal stability of biomass
as the inverse of the coefficient of variation. We further partitioned stability
into population stability ($S_{pop}$) and asynchrony ($\phi$) such as:

\begin{equation}
\begin{aligned}
S_{com} = S_{pop} \times \phi
(\#eq:scom)
\end{aligned}
\end{equation}

with $S_{com} = \mu_{tot} / \sigma_{tot}$, $S_{pop} = \mu_{tot} / \sum_i \sigma_i$,
$\phi = \sum_i \sigma_i / \sigma_{tot}$.

$\mu_{tot}$ and $\sigma_{tot}$ being respectively average total biomass and standard
deviation of total biomass.

To further get a mechanistic insight about the effects of stressors and food-web structure on stability,
we partionned asynchrony into statistical averaging effect (SAE) and compensatory
dynamics effect (CPE) [@zhao_biodiversity_2022]. SAE controls for ..., while CPE describes compensatory
dynamics emerging from species interactions and differential responses to
environmental stochasticity.

\begin{equation}
\begin{aligned}
S_{com} = S_{pop} \times SAE \times CPE
(\#eq:scom)
\end{aligned}
\end{equation}

\begin{equation}
\begin{aligned}
SAE = SAE_{even} \times EVN
(\#eq:sae)
\end{aligned}
\end{equation}

Statistical averaging effect is the share of asynchrony assuming that species are
independant, meaning that the variance total of the community is equal to the
sum of species variances only (i.e. species covariances are null). We can
define community stability ($S_{com, IP}$) in that scenario and then derive $SAE$.

\begin{equation}
\begin{aligned}
S_{com, IP} &= \dfrac{\mu_{tot}}{\sqrt{\sum_i \sigma^2_i}} = SAE \times S_{pop} \\
SAE &= \dfrac{S_{com, IP}}{S_{pop}} = \dfrac{\sum_i \sigma_i}{\sqrt{\sum_i \sigma^2_i}}\\
(\#eq:sae2)
\end{aligned}
\end{equation}

As SAE is further dependant of biomass evenness in food-webs, we
partionned $SAE$ into $SAE_{even}$ and evenness $EVN$, such as $SAE_{even} =
\sqrt{S}$ and $EVN = SAE / SAE_{even}$.

Compensatory dynamics in the food-webs is then the remaining part of asynchony:

\begin{equation}
\begin{aligned}
CPE &= \dfrac{S_{com}}{SAE \times S_{pop}} = \dfrac{\sqrt{\sum_i \sigma^2_i}}{\sigma_{tot}}\\
(\#eq:cpe)
\end{aligned}
\end{equation}

Compensatory dynamics can arise from predator-prey interactions
($CPE_{int}$) or from differential response of species to enviromental
stochasticity ($CPE_{env}$). From the deterministic and stochastic parts of
mortality rates, we computed the compensatory dynamics linked to the environment
such as:

\begin{equation}
\begin{aligned}
CPE_{env} = \mathbf{B} \times \mathrm{diag}(d_i) \times e^\mathbf{E}
(\#eq:cpenv)
\end{aligned}
\end{equation}

with $\mathbf{B}$ and $\mathbf{E}$ being the matrices time x species for species biomass
and stochastic mortality rates respectively. Then compensatory dynamics raising
from species interactions were computed as: $CPE_{int} = CPE / CPE_{env}$.

## Statistical analysis

Using a structural equation model, we disantengled the complex effects of
food-web structure, environmental stochasticity and response diversity on the
different facets of temporal stability of biomass (i.e. population stability,
statistical averaging effects and compensatory dynamic effects). We set the
paths of the path of the model according to theorical expectations. We tested
the effects of species richness, connectance, and the Predator-Prey size ratio
on secondary structure of the food-webs, the average trophic level, the average
omnivory and the interaction strength. We also tested the effects of  on  We
expected that richness affect population stability by modifying the average
population biomass for exemple [@thibaut_understanding_2013]. Grounded in
theoretical ecological, we expected that average trophic level, the average
omnivory and the interaction strength modulated population stability
[@mccann_weak_1998; @mccann_reevaluating_1997; @shanafelt_stability_2018].
Previous studies have also the Predator-Prey size ratio modulate population
stability [@brose_allometric_2006]. Finally, the effect of enviromental
stochasticity was assumed to be mainly associated to population stability (i.e.
by increasing amplitude of population fluctuations).

Regarding asynchrony, we tested the effects of species richness, connectance,
weighted average trophic level and interaction strength on the evenness of
biomass which in turn affect total statistical averaging effects. We expected
that those same food-web structural properties also affected compensatory
dynamics due to interactions ($CPE_{int}$). Finally, we tested the effects of
species richness and species cross-correlation in mortality rates on the
compensatory dynamics due to stochastic fluctuations ($CPE_{env}$). We completed
the structural equation model with the mathematical relationship linking
compensatory dynamics and statistical averaging effects to asynchrony, and from
asynchrony and population stability to community stability.

Prior to test the structural equation model, we logged all the stability
components to transform their relation from multiplicative to additive (eq XX).
We ensure that all the linear models composing the structural equation model
presented low multicollinearity (Variance Inflation Factor < 5, Table SXX). The
structural equation model using the R package `PiecewiseSEM`
[@lefcheck_piecewisesem_2016]. We then bootstrapped (N = 100) the SEM to obtain
confidence interval on the estimated effects and computed the sum of the direct
and indirect effects using `semEff` R package [@murphy_semeff_2021]. In the
main text, we reported standardized coefficients which are obtained by scaling
the coefficients by the stardard deviation of the response and predictor
variable (add formula). Finally, because we analyzed simulation, we reported
only the direct standardized coefficients that had an absolute value above $0.1$.

In a second analysis, we aimed to test how stability-species richness
relationships were modulated by food-web structure and the two stressors:
environmental stochasticity and response diversity. We modelled temporal
stability of biomass according to food-web structure: species richness, weighted average trophic
level, connectance, hill exponent, predator-prey size ratio, and average
interaction strength, as well as enviromental stochasticity and species
cross-correlation. We further included the two way interactions between species
richness and food-web structure, plus between species richness and stressors.
Finally we added the three way interaction between species richness, food-web
structure and stressors. The VIF were inferior to 5, indicating low
multicollinearity.


# Results

## Drivers of stability

```{r}
sem_cap <- paste0("Structural equation model. Only standardized coefficients
  whose absolute values are superior to 0.1 are displayed. [To complete with the links from initial structure]")
```

```{r sem, fig.cap=sem_cap}
knitr::include_graphics(here("report", "figures", "sem_stab2.pdf"))
```

```{r}
tar_load(sem_eff_tab)

get_eff <- function(y = "pop_stab", x = "richness", d = 2, effect_type = "direct") {
  mask <- sem_eff_tab$response == y & sem_eff_tab$predictor == x &
    sem_eff_tab$effect_type == effect_type
  round(sem_eff_tab[mask, ]$effect, d)
}

rpt <- get_eff(y = "pop_stab", x = "w_avg_tlvl")
rph <- get_eff(y = "pop_stab", x = "h")
rpe <- get_eff(y = "pop_stab", x = "env_stoch")
rsr <- get_eff(y = "sae_even", x = "richness")
ret <- get_eff(y = "evenness_sae", x = "w_avg_tlvl")
rer <- get_eff(y = "evenness_sae", x = "richness")
rea <- get_eff(y = "evenness_sae", x = "avg_int_strength")
rec <- get_eff(y = "evenness_sae", x = "ct_alive")
reh <- get_eff(y = "evenness_sae", x = "h")

ria <- get_eff(y = "cpe_int", x = "avg_int_strength")
ric <- get_eff(y = "cpe_int", x = "ct_alive")
rih <- get_eff(y = "cpe_int", x = "h")
rir <- get_eff(y = "cpe_int", x = "richness")

rvr <- get_eff(y = "cpe_env", x = "richness")
rvo <- get_eff(y = "cpe_env", x = "rho")
```
```{r, eval = FALSE}
sem_eff_tab %>%
  filter(abs(effect) > .1, effect_type == "direct")
```


We found that food-web structure had significant effect on temporal population
stability such as average trophic level and type III functional response (i.e. h = 3)
increase population stability (resp. $r_\delta$= `r rpt` and `r rph`, $r_\delta$
being the standardized coefficient, Fig. \@ref(fig:sem)). However the strength
of environmental stochasticity had a strong negative effect on population
stability ($r_\delta$= `r rpe`).

We further found that food-web structure had a strong impact on statistical
averaging effects, which raises from independant species fluctuations weigthed
the evenness of their biomass. As expected the mathematical relationship (eq. XX),
species richness was the only driver of even statistical averaging effect
($r_\delta$= `r rsr`, Fig. \@ref(fig:sem)). Average trophic level had a strong negative effect on
evenness ($r_\delta$= `r ret`), meaning that biomass are more inequally
distributed among species, thereby downplaying the portefolio effect raised from
species richness. But richness had also a small negative effect on evenness
($r_\delta$= `r rer`). Constrastingly, connectance, average interaction
strength, and type III functional response all increased biomass evenness
(resp. $r_\delta$= `r rec`, `r rea`, and `r reh`).

Food-web structure and cross-correlation among species mortality rates had
strong effects on compensatory dynamics. Average trophic level, connectance and
type III functional response had a negative effect on compensatory effect
raising from species interaction (resp. $r_\delta$= `r ria`, `r ric`, `r rih`,
Fig. \@ref(fig:sem)) there decreasing asynchony, while richness had a positive
effect ($r_\delta$= `r rir`), there increasingasynchrony. In turn, richness and
cross-correlation among species mortality rates had a negative effect on
compensatory dynamic raising from environmental stochasticity
($r_\delta$= `r rvr` and `r rvo`).

```{r}
rscp <- get_eff(y = "stab_com", x = "pop_stab")
rsca <- get_eff(y = "stab_com", x = "async")

rav <- get_eff(y = "async", x = "cpe_env")
rae <- get_eff(y = "async", x = "evenness_sae")

rass <- get_eff(y = "async", x = "sae_even")
rasi <- get_eff(y = "async", x = "cpe_int")
```


Population stability had a positive effect twice higher than asynchrony on the
temporal stability of community (resp. $r_\delta$= `r rscp` and `r rsca`). In turn, asynchrony
was mostly driven by evenness of biomass distribution and compensatory dynamics
raising from environmental stochasticity (resp. $r_\delta$= `r rae` and `r rav`, Fig.
\@ref(fig:sem)) than from statistical averaging emerging from species richness
(i.e. even) and compensatory dynamics emerging from species interaction (resp.
$r_\delta$= `r rass` and `r rasi`).

```{r}
semtot_cap <- "Total effect of food-web structure and stressors on community
stability, asynchony, and population stability. The total effects were derived
from the structural equation model."
```


```{r semtot, fig.cap = semtot_cap}
tar_read(p_sem_tot_stab)
```

Deriving the sum of direct and indirect effects from the structural equation
model, we show that both enviromental stochasticity and cross-correlation among
species had by far the most negative effect on community stability (XX, Fig.
\@ref(fig:semtot)). Average trophic level, type III functional response and
predator prey bodysize ratio had total positive effects on community stability.
Those positive effects are raising from sometimes contrasting effects on
population stability and asynchrony such as Average trophic level, type III
functional response and predator prey bodysize ratio which have positive effects
on population stability (resp. XXX) but a negative one on asynchrony (resp. XXX).


## Stability-richness relationship

```{r}
pred_cap <- "Relationship between community stability and species richness
according to environmental stochasticity and response diversity. (a) Simulation [add parameters selected], (b) Prediction from the linear model. "
```


```{r pred, fig.cap = pred_cap}
knitr::include_graphics(here("report", "figures", "p_sim_pred.pdf"))
```

Using a more complex linear model (i.e. containing interaction), we investigated more
in detail the relationship between community stability and species richness and
how this relation is affected by environmental stochasticity and cross
correlation among species mortality rates. We found that environmental
stochasticity decrease overall community stability but does not change the shape
of the community stability-species richness relationship (put some numbers, Fig.
\@ref(fig:pred)a and b). In contrasts, cross correlation among species mortality rates
both decreases overall community stability and nullifies the community
stability-species richness relationship. Surpringly, we found that
despite average interaction strength has a small overall effect on
community stability, high average interaction strength change the shape of the
community stability-species richness relationship from positive to negative when
response diversity is low (put some numbers, Fig. \@ref(fig:pred)b).


```{r, eval = FALSE}
tar_read(p_int_fw_str)
```

# Discussion

## Food-web structure and stressors affects population stability and asynchony

Our results shows that community stability in complex food-webs is mainly driven
by population stability rather than synchrony, confirming previous results in
empirical data [@danet_species_2021]. We further found that average trophic
level and functional response of type III increased average population
stability, confirming previous results [@brose_allometric_2006;
@shanafelt_stability_2018; @danet_species_2021;
@eschenbrenner_diversity_nodate]. Higher average trophic level stabilises
populations because higher predator are themselves more stable and because they
control the amplitude of the fluctuations of their prey [REF, we can test
that?]. Furthermore, average omnivory was strongly correlated with average
trophic level, suggesting that average omnivory also stabilise population
stability, in line with previous theoretical results in small modules
[@mccann_reevaluating_1997]. In turn, functional response of type III decreases
the feeding rates of consumers when their preys have a low biomass which leads
to a less dramatic fluctuations of prey biomass [@uszco_effects_2017;
@brose_allometric_2006]. We however found no big effect of species richness on
population stability, which has been reported to be negative, positive or
neutral in previous studies [@ruijven_contrasting_2007;
@houlahan_negative_2018].

Our results shows that asynchrony is mainly decreased by the cross-correlation
among species mortality rates and mediated by compensatory dynamics, indicating
that the loss of response diversity suppressed the positive effects of species
richness on stability. Our result shows that evenness of biomass plays an
significant role in driving statistical averaging effect (i.e. portefolio
effects). Our results shows that average trophic level decreases strongly the
evenness of biomass variability, thereby limiting the effect of species richness on the
portefolio effects. Furthermore, increase in species richness also resulted in
less even biomass variability. Our results also suggest that stronger species
interaction, higher generalism, and functional response of type III are
associated with a more even variability, thereby raising the portefolio
effects. The importance of evenness in driving portefolio effects has been
recognised early by theoretical studies [@thibaut_understanding_2013], but
rather in terms of abundance than in variability [@zhao_biodiversity_2022].
We suggest that higher average trophic level decreases evenness of variability
because the model assumes that species of higher trophic level have a lower
overall mortality rates, similarly to previous studies [@vasseur_environmental_2007].

Our results further suggest that higher average trophic level results in lower
compensatory dynamics raising from species interactions. It might be explained
by the fact that average trophic level is strongly associated with average
omnivory, which might tamper synchronized predator-prey oscillations that can
raise compensatory dynamics [@mccann_reevaluating_1997]. Higher generalism in
also drives lower compensatory dynamics due to species interaction and then lend
to the same hypothesis such as more trophic links per consumer should decrease
overall amplitude of oscillations due to prey switching. Furthermore, functional
response of type III which drives prey switching at low abundance of the
prefered prey also lend toward this interpretation
[@mccann_diversitystability_2000]. [Do not have clear idea for richness at this
time]. Surpringly however, average interaction strength had no effects on
compensatory dynamics that is not already captured by other food-web structural
properties. Compensatory dynamics due to environment was decreased by both
species richness and cross-correlation among species mortality rates (i.e. loss
of response diversity). Our interpretation is that higher species richness
syncronize more species fluctuations due to mortality because each added species
adds (S - 1, S being richness) positive covariance terms in the stochastic
mortality rates, thereby increasing the overall synchrony in mortality rates
when cross correlation are not null.

## Stochasticity and response diversity affect stability-richness relationship

Our results suggest that, confirming the result of the structural equation
model, that in maximal response diversity environmental stochasticity primarily
drives average stability, without changing the shape of the stability-richess
relationship. The reason is that the strength of environmental stochasticity
only affect population stability and not asynchrony, the latter being the driver
of species-richness relationships. In turn, a decrease in response diversity
dampens the stability-richness relationship [@thibaut_understanding_2013].
Interestingly, our results also suggest that high response diversity also
decrease the destabilising effects of average interaction strength on
stability-richness relationships. Indeed, in low response diversity, we found
high interaction strength leads to negative stability-richness relationships.

## Implication for real world

Our results highlight that population stability is the primary driver of
community stability. In the context of global changes in which environmental
variability is expected to increase tremendously, we expect to see a strong
decrease in community stability, despite high response diversity. But ongoing
biotic homogenization [@olden_homogocene_2018; @muthukrishnan_invasive_2020;
@wang_biotic_2021] is also suggested to descrease response diversity
[@wang_biotic_2021; @su_human_2021], which in turn is expected to further
decrease stability despite high species richness, even more in food-web
communities composed of high interaction strength. Then, our study reinforces
that the restauration of ecosystems along with a restauration of landscape
complexity that provides refuges from extrem environment are key to maintain
temporal stability of ecological communities [@ryser_landscape_2021].

# Conclusion

TODO

# References {-}
