---
title: Response diversity is a major driver of temporal stability in complex food webs
author: "Alain Danet (1,2), Sonia Kéfi (3,4), Thomas F. Johnson (1), Andrew P. Beckerman (1)"
date: ""
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    keep_tex: true
    spacing: double
    number_sections: false
  officedown::rdocx_document:
    number_sections: false
    base_format: "bookdown::word_document2"
always_allow_html: true
bibliography: references.bib
toc: false
linestretch: 2.0
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{hyperref}
  - \hypersetup{backref=true}
  - \usepackage{setspace}\doublespacing
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.pos = "H",  # pdf mode
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE,
  fig.path="figures/"
)
```

```{r, results = FALSE}
sapply(c("targets", "tidyverse", "magrittr", "cowplot", "here", "piecewiseSEM",
    "semEff", "ggcorrplot", "kableExtra", "rmarkdown", "officedown"),
  require,
  character.only = TRUE)
mytheme <- theme_cowplot(font_size = 8) +
background_grid() +
theme(legend.position = "bottom")
theme_set(mytheme)
sapply(list.files(here("R"), full.names = TRUE), source)
```

```{=latex}
\begin{singlespace}
```
- 1 School of Biosciences, Ecology and Evolutionary Biology, University of Sheffield, Western Bank, Sheffield, S10 2TN, UK
- 2 DECOD (Ecosystem Dynamics and Sustainability), INRAE, Institut Agro, IFREMER, Rennes, France
- 3 ISEM, CNRS, Univ. Montpellier, IRD, EPHE, Montpellier, France
- 4 Santa Fe Institute, 1399 Hyde Park Road, Santa Fe, NM 87501, USA

- Email address:
  - Alain Danet (corresponding author): alain.danet@inrae.fr
  - Sonia Kéfi: sonia.kefi@umontpellier.fr
  - Thomas F Johnson: t.f.johnson@sheffield.ac.uk
  - Andrew P Beckerman: a.beckerman@sheffield.ac.uk

- Short running title: Response diversity drives food web stability

- Keywords: food webs, temporal stability, theoretical modelling, response
  diversity

- Type of article: Research

- Number of words: Abstract: 177, Main text: 6965

- Number of references: 68, Number of figures: 2, Number of tables: 0

- Corresponding author: Alain Danet, School of Biosciences, Ecology and
  Evolutionary Biology, University of Sheffield, Western Bank, Sheffield, S10
  2TN, UK; e-mail address: alain.danet@inrae.fr

Statement of authorship: AD and APB designed the research, AD performed the
research. AD wrote the first draft of the manuscript. All authors contributed
substantially to revisions.

Data accessibility statement: The code used to run the simulations, analyse them
and to write the manuscript is archived on Zenodo:
https://zenodo.org/records/16745483.

# Acknowledgements

We thank Owen Petchey and Tanya Strydom for their constructive feedback on the
study. AD, TFJ and APB have received support from the Natural Environment
Research Council under grant agreement no. NE/T003502/1 awarded to APB.

```{=latex}
\end{singlespace}
```
